---
title: "Cage Data Checks"
output:
  html_document:
params:
    Sites: ["CR", "SL", "LX"]
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2025-06-01")  # Start Date for Checks
CheckEnd <- as.Date("2025-07-28")  # End Date for Checks
DataManager = "Erica Williams"
Database = "Oysters_25-07-23"
Server = "localhost\\ERICALOCALSQL"

EstuaryCode = params$Sites #params$Sites  #params$Sites for multiple or use 2-letter code in Primary Keys for single

```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(rMR)
library(scales)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 10pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 19pt;
font-weight: bold;
}

h2 {
font-size: 15pt;
font-weight: bold;
}

h3 {
font-size: 13pt;
font-style: italic;
}

h4 {
font-size: 11pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary %in% EstuaryCode)

hsdbTripInfo <- tbl(con,in_schema("hsdb", "TripInfo")) %>%
  collect() 

dboTripInfo <- tbl(con,in_schema("dbo", "TripInfo")) %>%
  collect() 
  
hsdbSampleEvent <- tbl(con,in_schema("hsdb", "SampleEvent")) %>%
  collect() 
  
dboSampleEvent <- tbl(con,in_schema("dbo", "SampleEvent")) %>%
  collect() 

hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() 

dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() 

hsdbCageCount <- tbl(con,in_schema("hsdb", "CageCount")) %>%
  collect() 

dboCageCount <- tbl(con,in_schema("dbo", "CageCount")) %>%
  collect()

hsdbCageSH <- tbl(con,in_schema("hsdb", "CageSH")) %>%
  collect() 

dboCageSH <- tbl(con,in_schema("dbo", "CageSH")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Cage data in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()
          
hsdbTripInfo <- hsdbTripInfo %>% 
  filter(substring(TripID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "CAGE")  %>%
  arrange(TripID)

TripInfo1 <- dboTripInfo %>% 
  filter(substring(TripID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "CAGE" & DataStatus == "Proofed") %>%
  arrange(TripID)

TripInfo2 <- TripInfo1 %>%
  select(TripID, TripDate, Comments) %>%
  arrange(TripID)

hsdbSampleEvent <- hsdbSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "CAGE") %>%
  arrange(TripDate)

SampleEvent1 <- dboSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "CAGE" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber)

hsdbSampleEventWQ <- hsdbSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventWQID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "CAGE") %>%
  arrange(TripDate)

SampleEventWQ1 <- dboSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventWQID, 19, 22)) %>%
  filter(substring(SampleEventWQID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "CAGE" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEventWQ1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, SampleEventWQID)

hsdbCounts <- hsdbCageCount %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "CAGE") %>%
  arrange(TripDate)

Counts1 <- dboCageCount %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(CageCountID, 19, 22),
         CageID = substring(CageCountID, 28, 28)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, Counts1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, CageCountID) 


hsdbSH <- hsdbCageSH %>% 
  mutate(TripDate = as.Date(substring(CageCountID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(CageCountID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(CageCountID,3,6) == "CAGE") %>%
  arrange(TripDate)

SH1 <- dboCageSH %>%
  mutate(TripDate = as.Date(substring(CageCountID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(CageCountID, 19, 22),
         CageID = substring(CageCountID, 28, 28),
         DataType = substring(CageCountID, 26, 26),
         ShellHeight = as.integer(ShellHeight)) %>%
    filter(substring(CageCountID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, Counts1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, ShellHeightID) 

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the dbo schema
ERR_Table1 <- data.frame()
ERR_Table1a <- data.frame()
ERR_Table1b <- data.frame()
ERR_Table1c <- data.frame()
ERR_Table1d <- data.frame()
ERR_Table1e <- data.frame()

if (nrow(TripInfo1[duplicated(TripInfo1$TripID), ]) > 0) {
  ERR_Table1a <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "TripInfo", TripInfo1[duplicated(TripInfo1$TripID), ])) %>% 
    mutate(PrimaryKey = TripID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEvent1[duplicated(SampleEvent1$SampleEventID), ]) > 0) {
  ERR_Table1b <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEvent", SampleEvent1[duplicated(SampleEvent1$SampleEventID), ])) %>% 
    mutate(PrimaryKey = SampleEventID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ]) > 0) {
  ERR_Table1c <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEventWQ", SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ])) %>% 
    mutate(PrimaryKey = SampleEventWQID) %>% 
    select(schema, Table, PrimaryKey)
}

if (nrow(Counts1[duplicated(Counts1$CageCountID), ]) > 0) {
  ERR_Table1d <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "CageCounts", Counts1[duplicated(Counts1$CageCountID), ])) %>% 
    mutate(PrimaryKey = ShellID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SH1[duplicated(SH1$ShellHeightID), ]) > 0) {
  ERR_Table1e <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "CageSHs", SH1[duplicated(SH1$ShellHeightID), ])) %>% 
    mutate(PrimaryKey = ShellHeightID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Tablex <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, Counts1$CageCountID, SH1$ShellHeightID)
dest <- list(hsdbTripInfo$TripID, hsdbSampleEvent$SampleEventID, hsdbSampleEventWQ$SampleEventWQID, hsdbCageCount$CageCountID, hsdbCageSH$ShellHeightID)
tabl <- list("TripInfo", "SampleEvent", "SampleEventWQ", "CageCounts", "CageSHs")

# Loop through values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if ((check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Tablex <- rbind(ERR_Tablex, data.frame(schema = "hsdb", Table = tabl[[i]], PrimaryKey = check_id))
    }
  }
}

ERR_Table1 <- rbind(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Tablex)
rm(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Tablex)


### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Counts1$SampleEventID, SH1$CageCountID)
dest <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, Counts1$CageCountID)
tabl <- list("SampleEvent", "SampleEventWQ", "CageCounts", "CageSHs")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if (!(check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless
ERR_Table3 <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, Counts1$CageCountID)
dest <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Counts1$SampleEventID, SH1$CageCountID)
tabl <- list("TripInfo", "SampleEvent", "SampleEvent", "CageCounts")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
    if (!(check_id %in% dest[[i]])) {
      ERR_Table3 <- rbind(ERR_Table3, data.frame(Table = tabl[[i]], ChildlessPrimaryKey = check_id))
    }
  }
}
ERR_Table3 <- distinct(ERR_Table3) 

# Ensure there are 6 cages per SampleEvent for all Sites (3 deployed/3 retrieved)
# Counts up the number of cages that were made
ERR_Table3a <- left_join(as.data.frame(table((Counts1 %>% filter(DataType == "Deployed"))$SampleEventID)) %>%  rename("SampleEventID" = "Var1", "Deployed" = "Freq"), 
                         as.data.frame(table((Counts1 %>% filter(DataType == "Retrieved"))$SampleEventID)) %>%  rename("SampleEventID" = "Var1", "Retrieved" = "Freq")) %>% 
  filter(Deployed < 3 | Retrieved < 3) %>% merge(Counts1 %>% dplyr::select(SampleEventID, Comments))

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly
ERR_Table4 <- data.frame()
pkid <- list(SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, Counts1$CageCountID, SH1$ShellHeightID)
fkid <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Counts1$SampleEventID, SH1$CageCountID)
tabl <- list("SampleEvent", "SampleEventWQ", "CageCounts", "CageSHs")
numb <- list(17, 24, 24, 28)

for (i in seq_along(pkid)) {
  for (j in seq_along(fkid[[i]])) {
    check_fkid <- fkid[[i]][j]
    check_pkid <- substring(pkid[[i]][j],1,numb[[i]])
    if (check_fkid != check_pkid) {
      ERR_Table4 <- rbind(ERR_Table4, data.frame(Table = tabl[[i]], PrimaryKey = pkid[[i]][j], ForeignKey = check_fkid))
    }
  }
}

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
TripInfo_nulls <- filter(TripInfo1, is.na(TripID) | is.na(TripType) | is.na(TripDate) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(TripID, TripDate, TripType, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEvent_nulls <- filter(SampleEvent1, is.na(SampleEventID) | is.na(TripID) | is.na(FixedLocationID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventID, TripID, FixedLocationID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEventWQ_nulls <- filter(SampleEventWQ1, is.na(SampleEventWQID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventWQID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

CageCount_nulls <- filter(Counts1, is.na(CageCountID) | is.na(SampleEventID) | is.na(DeployedDate) |is.na(CageColor) | is.na(TotalCount) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(CageCountID, SampleEventID, DeployedDate, CageColor, TotalCount, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

CageSH_nulls <- filter(SH1, is.na(ShellHeightID) | is.na(CageCountID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(ShellHeightID, CageCountID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

# Remove unneeded data frames and values

rm(dboFixedLocations, dboCageCount, dboCageSH, dboSampleEvent, dboSampleEventWQ, dboTripInfo, dest, FixedLocations1, hsdbCageCount, hsdbCageSH, hsdbSampleEvent, hsdbSampleEventWQ, hsdbTripInfo, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table3) > 0 | nrow(ERR_Table3a) > 0 | nrow(ERR_Table4) > 0 | nrow(TripInfo_nulls) > 0 | nrow(SampleEvent_nulls) > 0 | nrow(SampleEventWQ_nulls) > 0 | nrow(CageCount_nulls) > 0 | nrow(CageSH_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## TripInfo #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## SampleEvent #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## Water Quality #
  # Unexpected Null values

null_WQs <- filter(SampleEventWQ1, is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(Depth) | is.na(SampleDepth) | is.na(PercentDissolvedOxygen)) %>% filter(!grepl(paste(c("ame as", "ame WQ", "ame Water", "ame water"), collapse = '|'), Comments)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Temperature, Salinity, DissolvedOxygen, PercentDissolvedOxygen, pH, Comments)

  # Out of range values
Temp_range <- filter(SampleEventWQ1, Temperature < 10 | Temperature > 34) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Temperature, Comments)
Sal_range <- filter(SampleEventWQ1, Salinity < 0.5 | Salinity > 38) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Salinity, Comments)
DO_range <- SampleEventWQ1 %>% 
  mutate(DO.Sat = DO.saturation(DO.mgl = DissolvedOxygen, temp.C = Temperature, elevation.m = 0, salinity = Salinity)) %>%
  filter(DO.Sat < 0.50 | DO.Sat > 1.50) %>%
  mutate(DO.Sat = percent(DO.Sat, accuracy = 1)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, DO.Sat, Comments)
DOPct_range <- SampleEventWQ1 %>% 
  filter(PercentDissolvedOxygen < 20 | PercentDissolvedOxygen > 150) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, PercentDissolvedOxygen, Comments)
pH_range <- filter(SampleEventWQ1, pH < 7.0 | pH > 8.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, pH, Comments)
Depth_range <- filter(SampleEventWQ1, Depth < 0 | Depth > 3.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
SampleDepth_range <- filter(SampleEventWQ1, SampleDepth < 0 | SampleDepth > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
Secchi_range <- filter(SampleEventWQ1, Secchi < 0 | Secchi > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Secchi, Comments)
TurbidityYSI_range <- filter(SampleEventWQ1, TurbidityYSI < -2 | TurbidityYSI > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityYSI, Comments)
TurbidityHach_range <- filter(SampleEventWQ1, TurbidityHach < -2 | TurbidityHach > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityHach, Comments)

## Cage Counts #
  # Unexpected Null values
# We should change it in ODIN so that empty strings aren't sent. They should be null instead. Then the following line won't be needed
Counts1$Comments <- ifelse(nchar(Counts1$Comments) == 0, NA, Counts1$Comments) 

null_Counts <- filter(Counts1, is.na(TotalCount) & is.na(Comments)) %>% select(CageCountID, DeployedDate, RetrievedDate, StationNumber, FixedLocationID, CageColor, TotalCount, Comments)

  # Out of range values
Days_range <- filter(Counts1, DaysDeployed < 20 | DaysDeployed > 36) %>%
  select(TripDate, DeployedDate, DaysDeployed, StationNumber, SampleEventID, Comments) %>%
  distinct()
Count_range <- filter(Counts1, TotalCount > 30 | (TotalCount < 30 & DataType == "Deployed") | (TotalCount < 1 & DataType == "Retrieved")) %>%
  select(TripDate, DeployedDate, StationNumber, CageColor, TotalCount, SampleEventID, Comments)

## SurveySH #
  # Unexpected Null values

SH1$Comments <- ifelse(nchar(SH1$Comments) == 0, NA, SH1$Comments)
null_SH <- left_join(Counts1, SH1, by = c("CageCountID")) %>%
  rename("Comments" = "Comments.x") %>%
  select(ShellHeightID, ShellHeight, TotalCount, Comments) %>%
  filter(is.na(ShellHeight) & TotalCount != 0) 

SH_range <- filter(SH1, ShellHeight < 1 | ShellHeight > 150) %>%
  select(ShellHeightID, ShellHeight, Comments) 


## Set error messages #

if (nrow(null_WQs) > 0) {
  Mess_null_WQs = ""
} else {
  Mess_null_WQs = "Congratulations! No unexpected null values detected."
}

if (nrow(Temp_range) > 0 | nrow(Sal_range) > 0 | nrow(DO_range) > 0 | nrow(pH_range) > 0 | nrow(Depth_range) > 0 | nrow(SampleDepth_range) > 0 | nrow(Secchi_range) > 0 | nrow(TurbidityYSI_range) > 0 | nrow(TurbidityHach_range)) {
  MessWQ_ranges = ""
} else {
  MessWQ_ranges = "Congratulations! No out of range values detected."
}

if (nrow(null_Counts) > 0) {
  Mess_null_Counts = ""
} else {
  Mess_null_Counts = "Congratulations! No unexpected null values detected."
}


if (nrow(Days_range) > 0 & nrow(Count_range) > 0) {
  MessRec_ranges = ""
} else {
  MessRec_ranges = "Congratulations! No out of range values detected."
}

if (nrow(null_SH) > 0) {
  Mess_null_SH = ""
} else {
  Mess_null_SH = "Congratulations! No unexpected null values detected."
}


if (nrow(SH_range) > 0) {
  MessCageSH_ranges = ""
} else {
  MessCageSH_ranges = "Congratulations! No out of range values detected."
}

#List of stored procedure lines
for(i in list(EstuaryCode)) {
  checks <- NULL
  checks[i] <- paste0("EXECUTE [dbo].[spChecksCage] @CheckStart = &apos;", CheckStart, "&apos;, @CheckEnd = &apos;", CheckEnd, "&apos;, @EstuaryCode = &apos;", i, "&apos;, @DataManager = &apos;", DataManager, "&apos;;")
  }
```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
for the site(s) <p2> `r EstuaryCode` </p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d.%B.%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! Only exception is on DEPLOY ONLY events.")}`

`r if (nrow(ERR_Table3a) > 0) {kable(ERR_Table3a, caption = "Childless Primary Keys. SampleEvents must have 6 total child records unless a valid comment is present.")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(CageCount_nulls) > 0) {kable(CageCount_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(CageSH_nulls) > 0) {kable(CageSH_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment required for all Null values")}`

<h4>--- Cage Counts ---</h4>

<p2>`r Mess_null_Counts`</p2>

`r if (nrow(null_Counts) > 0) {kable(null_Counts, caption = "Null Cage count data. Comment required for all Null values")}`

<h4>--- Cage Shell Heights ---</h4>

<p2>`r Mess_null_SH`</p2>

`r if (nrow(null_SH) > 0) {kable(null_SH, caption = "Null Cage shell height data. Null valules should only be recorded when no oysters were measured. ShellHeightID should end _01 and TotalCount should be 0. A comment may be required.")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 34.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 35.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range calculated dissolved oxygen data. Expected range is 50% to 150% saturation. Comment required for out of range values.")}`

`r if (nrow(DOPct_range) > 0) {kable(DOPct_range, caption = "Out of range percent dissolved oxygen data. Expected range is 20% to 150% saturation. Comment required for out of range values.")}`


`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Cage Counts ---</h4>

<p2>`r MessRec_ranges`</p2>

`r if (nrow(Days_range) > 0) {kable(Days_range, caption = "Out of range number of days deployed. Expected range is 20 to 36 days. Confirm out of range values. No comment required.")}`

`r if (nrow(Count_range) > 0) {kable(Count_range, caption = "Out of range Cage count data. Expected range is less than or equal to 30 oysters. Deployed cages should have 30 oysters. Retrieved cages should have 1 to 30 oysters. Comment required for out of range values.")}`

<h4>--- Cage Shell Heights ---</h4>

<p2>`r MessCageSH_ranges`</p2>

`r if (nrow(SH_range) > 0) {kable(SH_range, caption = "Out of range Shell Height data. Expected range for ShellHeight is 1 to 150 mm. Cannot be 0. Comment required for out of range values.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

`r paste(checks, collapse = "<br>")`

`r knit_exit()`

```{sql SQL code, eval=FALSE, include=TRUE}

--- This code creates a stored procedure in the database. 
-- To do so, copy and paste this code VERBATIM into SSMS
-- DO NOT RUN THIS CODE WITH R --

CREATE PROCEDURE [dbo].[spChecksCage](
	@CheckStart AS DATE,
	@CheckEnd AS DATE,
	@EstuaryCode AS VARCHAR(2),
	@DataManager AS VARCHAR(max)
	)
AS
BEGIN
	DECLARE @CompletedDate DATE;
	SET @CompletedDate = cast(getDate() as date);

	IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
	BEGIN
		DROP TABLE #ValidTrips;
	END

	CREATE TABLE #ValidTrips (
		TripID VARCHAR(50)
	);

	INSERT INTO #ValidTrips (TripID)
	SELECT TripID
	FROM TripInfo
	WHERE TripDate >= @CheckStart AND TripDate <= @CheckEnd
	AND DataStatus = 'Proofed' AND TripID like CONCAT(@EstuaryCode, 'CAGE%');

	-- Query the TripInfo table using the temporary table
	UPDATE dbo.TripInfo 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEvent table using the temporary table
	UPDATE dbo.SampleEvent 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEventWQ table using the temporary table
	UPDATE dbo.SampleEventWQ 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

	-- Query the CageCounts table using the temporary table
	UPDATE dbo.CageCounts 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));
	
	-- Query the CageSH table using the temporary table
	UPDATE dbo.CageSH 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE CageCountID IN (SELECT CageCountID FROM CageCount WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips)));

	-- Insert the Completed data into hsdb, and DELETE FROM dbo
	INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';

	DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';

	DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';

	DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.CageCount SELECT * FROM CageCount WHERE DataStatus = 'Completed';

	DELETE FROM dbo.CageCount WHERE DataStatus = 'Completed';

  INSERT INTO hsdb.CageSH SELECT * FROM CageSH WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.CageSH WHERE DataStatus = 'Completed';
END

```
