---
title: "Collections Data Checks"
subtitle: "Condition Index, Dermo, and Repro"
output:
  html_document:
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2023-01-01")  # Start Date for Checks
CheckEnd <- as.Date("2023-08-28")  # End Date for Checks
EstuaryCode = "AB"  # Estuary Code. Use 2-letter code in Primary Keys
DataManager = "Matthew Davis"
Database = "OysterLocalMD20231019"
```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(rMR)
library(scales)
library(geosphere)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 8pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 18pt;
font-weight: bold;
}

h2 {
font-size: 14pt;
font-weight: bold;
}

h3 {
font-size: 12pt;
font-style: italic;
}

h4 {
font-size: 10pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = "localhost\\MATTLOCALSQL",
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == EstuaryCode)

hsdbTripInfo <- tbl(con,in_schema("hsdb", "TripInfo")) %>%
  collect() 

dboTripInfo <- tbl(con,in_schema("dbo", "TripInfo")) %>%
  collect() 
  
hsdbSampleEvent <- tbl(con,in_schema("hsdb", "SampleEvent")) %>%
  collect() 
  
dboSampleEvent <- tbl(con,in_schema("dbo", "SampleEvent")) %>%
  collect() 

hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() 

dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() 

hsdbCI <- tbl(con,in_schema("hsdb", "ConditionIndex")) %>%
  collect() 

dboCI <- tbl(con,in_schema("dbo", "ConditionIndex")) %>%
  collect()

hsdbDermo <- tbl(con,in_schema("hsdb", "Dermo")) %>%
  collect() 

dboDermo <- tbl(con,in_schema("dbo", "Dermo")) %>%
  collect()

hsdbRepro <- tbl(con,in_schema("hsdb", "Repro")) %>%
  collect() 

dboRepro <- tbl(con,in_schema("dbo", "Repro")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Collections trips in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber),
         FixedLat = LatitudeDec,
         FixedLon = LongitudeDec) %>% 
  select(FixedLocationID, Estuary, SectionName, StationNumber, FixedLat, FixedLon) %>% 
  distinct()
          
TripInfo1 <- dboTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(TripID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripID)

TripInfo2 <- TripInfo1 %>%
  select(TripID, TripDate, Comments) %>%
  arrange(TripID)

SampleEvent1 <- dboSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber)

SampleEventWQ1 <- dboSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventWQID, 19, 22)) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventWQID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEventWQ1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, SampleEventWQID)

CI1 <- dboCI %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, CI1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)

Dermo1 <- dboDermo %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22),
         DermoMantle = as.numeric(DermoMantle),
         DermoGill = as.numeric(DermoGill)) %>% 
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, Dermo1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)

Repro1 <- dboRepro %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>% 
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, Repro1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)

hsdbTripInfo <- hsdbTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(TripID,3,6) == "COLL")  %>%
  arrange(TripID)

hsdbSampleEvent <- hsdbSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL") %>%
  arrange(TripDate)

hsdbSampleEventWQ <- hsdbSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventWQID,3,6) == "COLL") %>%
  arrange(TripDate)

hsdbCI <- hsdbCI %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

hsdbDermo <- hsdbDermo %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

hsdbRepro <- hsdbRepro %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the dbo schema
ERR_Table1 <- data.frame()
ERR_Table1a <- data.frame()
ERR_Table1b <- data.frame()
ERR_Table1c <- data.frame()
ERR_Table1d <- data.frame()
ERR_Table1e <- data.frame()
ERR_Table1f <- data.frame()

if (nrow(TripInfo1[duplicated(TripInfo1$TripID), ]) > 0) {
  ERR_Table1a <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "TripInfo", TripInfo1[duplicated(TripInfo1$TripID), ])) %>% 
    mutate(PrimaryKey = TripID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEvent1[duplicated(SampleEvent1$SampleEventID), ]) > 0) {
  ERR_Table1b <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEvent", SampleEvent1[duplicated(SampleEvent1$SampleEventID), ])) %>% 
    mutate(PrimaryKey = SampleEventID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ]) > 0) {
  ERR_Table1c <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEventWQ", SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ])) %>% 
    mutate(PrimaryKey = SampleEventWQID) %>% 
    select(schema, Table, PrimaryKey)
}

if (nrow(CI1[duplicated(CI1$OysterID), ]) > 0) {
  ERR_Table1d <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "ConditionIndex", SurveyQuadrat1[duplicated(CI1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(Dermo1[duplicated(Dermo1$OysterID), ]) > 0) {
  ERR_Table1e <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "Dermo", SurveySH1[duplicated(Dermo1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(Repro1[duplicated(Repro1$OysterID), ]) > 0) {
  ERR_Table1f <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "Repro", SurveySH1[duplicated(Repro1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Tablex <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, CI1$OysterID, Dermo1$OysterID, Repro1$OysterID)
dest <- list(hsdbTripInfo$TripID, hsdbSampleEvent$SampleEventID, hsdbSampleEventWQ$SampleEventWQID, hsdbCI$OysterID, hsdbDermo$OysterID, hsdbRepro$OysterID)
tabl <- list("TripInfo", "SampleEvent", "SampleEventWQ", "ConditionIndex", "Dermo", "Repro")

# Loop through values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if ((check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Tablex <- rbind(ERR_Tablex, data.frame(schema = "hsdb", Table = tabl[[i]], PrimaryKey = check_id))
    }
  }
}

ERR_Table1 <- rbind(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Table1f, ERR_Tablex)
rm(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Table1f, ERR_Tablex)


### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, CI1$SampleEventID, Dermo1$SampleEventID, Repro1$SampleEventID)
dest <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ", "ConditionIndex", "Dermo", "Repro")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if (!(check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless
ERR_Table3 <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
dest <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, CI1$SampleEventID, Dermo1$SampleEventID, Repro1$SampleEventID)
tabl <- list("TripInfo", "SampleEvent", "SampleEvent", "SampleEvent", "SampleEvent")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
    if (!(check_id %in% dest[[i]])) {
      ERR_Table3 <- rbind(ERR_Table3, data.frame(Table = tabl[[i]], ChildlessPrimaryKey = check_id))
    }
  }
}
ERR_Table3 <- distinct(ERR_Table3) 

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly
ERR_Table4 <- data.frame()
pkid <- list(SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID)
fkid <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ")
numb <- list(17, 24)

for (i in seq_along(pkid)) {
  for (j in seq_along(fkid[[i]])) {
    check_fkid <- fkid[[i]][j]
    check_pkid <- substring(pkid[[i]][j],1,numb[[i]])
    if (check_fkid != check_pkid) {
      ERR_Table4 <- rbind(ERR_Table4, data.frame(Table = tabl[[i]], PrimaryKey = pkid[[i]][j], ForeignKey = check_fkid))
    }
  }
}

# Ensure that Primary Keys and Foreign Keys have been formed correctly for OysterID in CI, Dermo, and Repro
ERR_Table4a <- CI1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "C", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

ERR_Table4b <- Dermo1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "D", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

ERR_Table4c <- Repro1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "D", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
TripInfo_nulls <- filter(TripInfo1, is.na(TripID) | is.na(TripType) | is.na(TripDate) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(TripID, TripDate, TripType, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEvent_nulls <- filter(SampleEvent1, is.na(SampleEventID) | is.na(TripID) | is.na(FixedLocationID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventID, TripID, FixedLocationID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEventWQ_nulls <- filter(SampleEventWQ1, is.na(SampleEventWQID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventWQID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

ConditionIndex_nulls <- filter(CI1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

Dermo_nulls <- filter(Dermo1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

Repro_nulls <- filter(Repro1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

# Remove unneeded data frames and values

rm(dboFixedLocations, dboRepro, dboDermo, dboCI, dboSampleEvent, dboSampleEventWQ, dboTripInfo, dest, FixedLocations1, hsdbRepro, hsdbDermo, hsdbCI, hsdbSampleEvent, hsdbSampleEventWQ, hsdbTripInfo, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table3) > 0 | nrow(ERR_Table4) > 0 | nrow(ERR_Table4a) > 0 | nrow(ERR_Table4b) > 0 | nrow(ERR_Table4c) > 0 | nrow(TripInfo_nulls) > 0 | nrow(SampleEvent_nulls) > 0 | nrow(SampleEventWQ_nulls) > 0 | nrow(ConditionIndex_nulls) > 0 | nrow(Dermo_nulls) > 0 | nrow(Repro_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## TripInfo #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## SampleEvent #
  # Unexpected Null values
null_SampleEvents <- filter(SampleEvent1, is.na(LatitudeDec) | is.na(LongitudeDec) | is.na(LatDec) | is.na(LatMin) | is.na(LongDec) | is.na(LongMin)) %>%
  select(SampleEventID, LatitudeDec, LongitudeDec, LatDec, LatMin, LongDec, LongMin)

  # Out of range values
SampleEvent_range <- SampleEvent1 %>%
  rowwise() %>%
  mutate(DistFromFixed = distVincentySphere(c(LongitudeDec, LatitudeDec), c(FixedLon, FixedLat))) %>%
  filter(DistFromFixed > 1852) %>% # Flags SampleEvents that occur over 1,852 meters (1 nautical mile) from the assigned FixedLocation.  
  select(SampleEventID, LatitudeDec, LongitudeDec, FixedLat, FixedLon, DistFromFixed)
  
## Water Quality #
  # Unexpected Null values
null_WQs <- filter(SampleEventWQ1, is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(Depth) | is.na(SampleDepth)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Temperature, Salinity, DissolvedOxygen, pH, Comments)

  # Out of range values
Temp_range <- filter(SampleEventWQ1, Temperature < 10 | Temperature > 33) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Temperature, Comments)
Sal_range <- filter(SampleEventWQ1, Salinity < 0.5 | Salinity > 35) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Salinity, Comments)
DO_range <- SampleEventWQ1 %>% 
  mutate(DO.Sat = DO.saturation(DO.mgl = DissolvedOxygen, temp.C = Temperature, elevation.m = 0, salinity = Salinity)) %>%
  filter(DO.Sat < 0.50 | DO.Sat > 1.20) %>%
  mutate(DO.Sat = percent(DO.Sat, accuracy = 1)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, DO.Sat, Comments)
pH_range <- filter(SampleEventWQ1, pH < 7.0 | pH > 8.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, pH, Comments)
Depth_range <- filter(SampleEventWQ1, Depth < 0 | Depth > 3.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
SampleDepth_range <- filter(SampleEventWQ1, SampleDepth < 0 | SampleDepth > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
Secchi_range <- filter(SampleEventWQ1, Secchi < 0 | Secchi > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Secchi, Comments)
TurbidityYSI_range <- filter(SampleEventWQ1, TurbidityYSI < -2 | TurbidityYSI > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityYSI, Comments)
TurbidityHach_range <- filter(SampleEventWQ1, TurbidityHach < -2 | TurbidityHach > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityHach, Comments)

## ConditionIndex #
  # Unexpected Null values
null_CI <- filter(CI1, is.na(ShellHeight), is.na(ShellLength), is.na(ShellWidth), is.na(TotalWeight), is.na(TarePanWeight), is.na(TissueWetWeight), is.na(ShellWetWeight), is.na(TissueDryWeight), is.na(ShellDryWeight)) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, TarePanWeight, TissueWetWeight, ShellWetWeight, TissueDryWeight, ShellDryWeight, Comments)

  # Out of range values
CI_range1 <- CI1 %>%
  mutate(Predicted.Weight = 0.0005 * (ShellHeight ^ 2.6434), #This calculation needs revisiting
         Pred.Vs.Actual = (Predicted.Weight - TotalWeight) / TotalWeight) %>%
  filter(ShellHeight < 10 | ShellHeight > 150 | ShellLength < 20 | ShellLength > 90 | ShellLength > ShellHeight | ShellWidth < 8 | ShellWidth > 50 | ShellWidth > ShellLength | Pred.Vs.Actual < -0.65 | Pred.Vs.Actual > 1.65) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, Predicted.Weight, Pred.Vs.Actual, Comments) 
CI_range2 <- filter(CI1, TarePanWeight < 0.9 | TarePanWeight > 5 | TissueWetWeight < ((TotalWeight + TarePanWeight) * 0.05) | TissueWetWeight > ((TotalWeight + TarePanWeight) * 0.4) | ShellWetWeight < (TotalWeight * 0.5) | ShellWetWeight > (TotalWeight * 0.99) | TissueDryWeight < TarePanWeight | TissueDryWeight > (TissueWetWeight * 0.9) | ShellDryWeight < (ShellWetWeight * 0.8) | ShellDryWeight > ShellWetWeight) %>%
  select(OysterID, TarePanWeight, TissueWetWeight, ShellWetWeight, TissueDryWeight, ShellDryWeight, Comments)

## Dermo #
  # Unexpected Null values
null_Dermo <- filter(Dermo1, is.na(ShellHeight), is.na(ShellLength), is.na(ShellWidth), is.na(TotalWeight), is.na(ShellWetWeight), is.na(DermoMantle), is.na(DermoGill)) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, ShellWetWeight, DermoMantle, DermoGill, Comments)

  # Out of range values
Dermo_range <- Dermo1 %>%
  mutate(Predicted.Weight = 0.0005 * (ShellHeight ^ 2.6434), #This calculation needs revisiting
         Pred.Vs.Actual = (Predicted.Weight - TotalWeight) / TotalWeight) %>%
  filter(ShellHeight < 10 | ShellHeight > 150 | ShellLength < 20 | ShellLength > 90 | ShellLength > ShellHeight | ShellWidth < 8 | ShellWidth > 50 | ShellWidth > ShellLength | Pred.Vs.Actual < -0.65 | Pred.Vs.Actual > 1.65 | DermoMantle < 0 | DermoMantle > 5 | DermoGill < 0 | DermoGill > 5) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, Predicted.Weight, Pred.Vs.Actual, DermoMantle, DermoGill, Comments)

## Repro #
  # Unexpected Null values
null_Repro <- filter(Repro1, is.na(Sex), is.na(Parasite), is.na(BadSlide)) %>%
  select(OysterID, Sex, ReproStage, Parasite, BadSlide, Comments)

  # Out of range values
Repro_range <- Repro1 %>%
  filter((Sex == "M/F" & !is.na(ReproStage)) | (Parasite == "Buceph" & !is.na(ReproStage)) | (ReproStage == 4 & Sex != "Z")) %>%
  select(OysterID, Sex, ReproStage, Parasite, BadSlide, Comments)

## Set error messages #

if (nrow(null_SampleEvents) > 0) {
  Mess_null_SampleEvents = ""
} else {
  Mess_null_SampleEvents = "Congratulations! No unexpected null values detected."
}
  
if (nrow(null_WQs) > 0) {
  Mess_null_WQs = ""
} else {
  Mess_null_WQs = "Congratulations! No unexpected null values detected."
}

if (nrow(null_CI) > 0) {
  Mess_null_CI = ""
} else {
  Mess_null_CI = "Congratulations! No unexpected null values detected."
}

if (nrow(null_Dermo) > 0) {
  Mess_null_Dermo = ""
} else {
  Mess_null_Dermo = "Congratulations! No unexpected null values detected."
}

if (nrow(null_Repro) > 0) {
  Mess_null_Repro = ""
} else {
  Mess_null_Repro = "Congratulations! No unexpected null values detected."
}

if (nrow(SampleEvent_range) > 0) {
  MessSampleEvent_ranges = ""
} else {
  MessSampleEvent_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Temp_range) > 0 | nrow(Sal_range) > 0 | nrow(DO_range) > 0 | nrow(pH_range) > 0 | nrow(Depth_range) > 0 | nrow(SampleDepth_range) > 0 | nrow(Secchi_range) > 0 | nrow(TurbidityYSI_range) > 0 | nrow(TurbidityHach_range)) {
  MessWQ_ranges = ""
} else {
  MessWQ_ranges = "Congratulations! No out of range values detected."
}

if (nrow(CI_range1) > 0 | nrow(CI_range2) > 0) {
  MessCI_ranges = ""
} else {
  MessCI_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Dermo_range) > 0) {
  MessDermo_ranges = ""
} else {
  MessDermo_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Repro_range) > 0) {
  MessRepro_ranges = ""
} else {
  MessRepro_ranges = "Congratulations! No out of range values detected."
}
```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d.%B.%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! SampleEvents must have 15 child records unless a valid comment is present.")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4a) > 0) {kable(ERR_Table4a, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4b) > 0) {kable(ERR_Table4b, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4c) > 0) {kable(ERR_Table4c, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(ConditionIndex_nulls) > 0) {kable(ConditionIndex_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Dermo_nulls) > 0) {kable(Dermo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Repro_nulls) > 0) {kable(Repro_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Sample Event ---</h4>

<p2>`r Mess_null_SampleEvents`</p2>

`r if (nrow(null_SampleEvents) > 0) {kable(null_SampleEvents, caption = "Null Sample Event Data. Comment Required for all Null values")}`

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment Required for all Null values")}`

<h4>--- Condition Index ---</h4>

<p2>`r Mess_null_CI`</p2>

`r if (nrow(null_CI) > 0) {kable(null_CI, caption = "Null Condition Index Data. Comment Required for all Null values")}`

<h4>--- Dermo ---</h4>

<p2>`r Mess_null_Dermo`</p2>

`r if (nrow(null_Dermo) > 0) {kable(null_Dermo, caption = "Null Dermo Data. Comment Required for all Null values")}`

<h4>--- Repro ---</h4>

<p2>`r Mess_null_Repro`</p2>

`r if (nrow(null_Repro) > 0) {kable(null_Repro, caption = "Null Repro Data. Comment Required for all Null values")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.

<h4>--- Sample Event ---</h4>

<p2>`r MessSampleEvent_ranges`</p2>

`r if (nrow(SampleEvent_range) > 0) {kable(SampleEvent_range, caption = "Out of range distance from Fixed Location. Expected range is 1,852 meters (1 nautical mile). Comment required for out of range values.")}`

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 33.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 35.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range dissolved oxygen data. Expected range is 50% to 120% saturation. . Comment required for out of range values.")}`

`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Condition Index ---</h4>

<p2>`r MessCI_ranges`</p2>

`r if (nrow(CI_range1) > 0) {kable(CI_range1, caption = "Out of range Condition data. Expected range for ShellHeight is 10 to 150 mm. Expected range for ShellLength is 20 to 90 mm and is less than ShellHeight. Expected range for ShellWidth is 8 to 50 mm and is less than ShellLength. Expected range for Pred.Vs.Actual is -0.65 to 1.65. Comment required for out of range values.")}`

`r if (nrow(CI_range2) > 0) {kable(CI_range2, caption = "Out of range Condition data. Expected range for TarePanWeight is 0.9 to 5.0 g. Expected range for TissueWetWeight is 5% to 40% of the sum of TotalWeight and TarePanWeight. Expected range for ShellWetWeight is 50% to 99% of TotalWeight. Expected range for TissueDryWeight is greater than TarePanWeight and up to 90% of TissueWetWeight. Expected range for ShellDryWeight is 80% to 100% of ShellWetWeight. Comment required for out of range values.")}`

<h4>--- Dermo ---</h4>

<p2>`r MessDermo_ranges`</p2>

`r if (nrow(Dermo_range) > 0) {kable(Dermo_range, caption = "Out of range Dermo data. Expected range for ShellHeight is 10 to 150 mm. Expected range for ShellLength is 20 to 90 mm and is less than ShellHeight. Expected range for ShellWidth is 8 to 50 mm and is less than ShellLength. Expected range for Pred.Vs.Actual is -0.65 to 1.65. Expected ranges for DermoMantle and DermoGill is 0 to 5. Comment required for out of range values.")}`

<h4>--- Repro ---</h4>

<p2>`r MessRepro_ranges`</p2>

`r if (nrow(Repro_range) > 0) {kable(Repro_range, caption = "Out of range Repro data. If Sex = M/F, ReproStage MUST be Null. If Parasite = Buceph, ReproStage MUST be Null. If ReproStage = 4, Sex MUST = Z.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

\~\~\~\~ Note to self: The bulk of this code may be better as a Stored
Procedure. Then the SQL Code here would be:\
EXEC sp_CompleteSurvey \'`r EstuaryCode`\', \'`r CheckStart`\',
\'`r CheckEnd`\', \'`r DataManager`\';

\~\~\~\~ SQL code with comments in un-run chunk at end.

\~\~\~\~ End note

IF OBJECT_ID(\'tempdb..#ValidTrips\') IS NOT NULL BEGIN DROP TABLE
#ValidTrips; END

CREATE TABLE #ValidTrips ( TripID VARCHAR(50) );

INSERT INTO #ValidTrips (TripID) SELECT TripID FROM TripInfo WHERE
TripDate \> \'`r CheckStart`\' AND TripDate \< \'`r CheckEnd`\' AND
DataStatus = \'Proofed\' AND TripID like \'`r EstuaryCode`SRVY%\';

UPDATE TripInfo SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

UPDATE SampleEvent SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d.%B.%Y")`\'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

UPDATE SampleEventWQ SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

UPDATE SurveyQuadrat SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

UPDATE SurveySH SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE QuadratID IN (SELECT QuadratID FROM SurveyQuadrat WHERE 
SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips)));

INSERT INTO hsdb.TripInfo SELECT \* FROM TripInfo WHERE DataStatus =
\'Completed\';

DELETE FROM dbo.TripInfo WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SampleEvent SELECT \* FROM SampleEvent WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.SampleEvent WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SampleEventWQ SELECT \* FROM SampleEventWQ WHERE
DataStatus = \'Completed\';

DELETE FROM dbo.SampleEventWQ WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SurveyQuadrat SELECT \* FROM SurveyQuadrat WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.SurveyQuadrat WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SurveySH SELECT \* FROM SurveySH WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.SurveySH WHERE DataStatus = \'Completed\';

`r knit_exit()`

```{sql SQL code, eval=FALSE, include=FALSE}

-- Check that there is not already a temporary table to store valid TripIDs. If there is, DELETE it and create a clean temporary table
IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
BEGIN
    DROP TABLE #ValidTrips;
END

CREATE TABLE #ValidTrips (
    TripID VARCHAR(50)
);

INSERT INTO #ValidTrips (TripID)
SELECT TripID
FROM TripInfo
WHERE TripDate > '`r CheckStart`' AND TripDate < '`r CheckEnd`'
AND DataStatus = 'Proofed' AND TripID like '`r EstuaryCode`SRVY%';

-- Query the TripInfo table using the temporary table
UPDATE TripInfo 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

-- Query the SampleEvent table using the temporary table
UPDATE SampleEvent 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d.%B.%Y")`'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

-- Query the SampleEventWQ table using the temporary table
UPDATE SampleEventWQ 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Query the SurveyQuadrat table using the temporary table
UPDATE SurveyQuadrat 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Query the SurveySH table using the temporary table
UPDATE SurveySH 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE QuadratID IN (SELECT QuadratID FROM SurveyQuadrat WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips)));

-- Insert the Completed data into hsdb, and DELETE FROM dbo
INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';

DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';

DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';

DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SurveyQuadrat SELECT * FROM SurveyQuadrat WHERE DataStatus = 'Completed';

DELETE FROM dbo.SurveyQuadrat WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SurveySH SELECT * FROM SurveySH WHERE DataStatus = 'Completed';

DELETE FROM dbo.SurveySH WHERE DataStatus = 'Completed';

```
