---
title: "Collections Data Checks"
subtitle: "Condition Index, Dermo, and Repro"
output:
  html_document:
params:
    CERP: ["SL", "LX", "LW", "CR"] 
    PBC: "LW"
    TIG: ["TB", "CR"]
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2025-02-01")  # Start Date for Checks
CheckEnd <- as.Date("2025-02-28")  # End Date for Checks
DataManager = "Erica Williams"
Database = "Oysters_25-02-27"
Server = "localhost\\ERICALOCALSQL"

EstuaryCode = c(params$CERP, params$PBC)  #params$[project] or use 2-letter code in Primary Keys for single estuary

```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(rMR)
library(scales)
library(geosphere)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 10pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 19pt;
font-weight: bold;
}

h2 {
font-size: 15pt;
font-weight: bold;
}

h3 {
font-size: 13pt;
font-style: italic;
}

h4 {
font-size: 11pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary %in% EstuaryCode)

hsdbTripInfo <- tbl(con,in_schema("hsdb", "TripInfo")) %>%
  collect() 

dboTripInfo <- tbl(con,in_schema("dbo", "TripInfo")) %>%
  collect() 
  
hsdbSampleEvent <- tbl(con,in_schema("hsdb", "SampleEvent")) %>%
  collect() 
  
dboSampleEvent <- tbl(con,in_schema("dbo", "SampleEvent")) %>%
  collect() 

hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() 

dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() 

hsdbCI <- tbl(con,in_schema("hsdb", "ConditionIndex")) %>%
  collect() 

dboCI <- tbl(con,in_schema("dbo", "ConditionIndex")) %>%
  collect()

hsdbDermo <- tbl(con,in_schema("hsdb", "Dermo")) %>%
  collect() 

dboDermo <- tbl(con,in_schema("dbo", "Dermo")) %>%
  collect()

hsdbRepro <- tbl(con,in_schema("hsdb", "Repro")) %>%
  collect() 

dboRepro <- tbl(con,in_schema("dbo", "Repro")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Collections trips in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber),
         FixedLat = LatitudeDec,
         FixedLon = LongitudeDec) %>% 
  select(FixedLocationID, Estuary, SectionName, StationNumber, FixedLat, FixedLon) %>% 
  distinct()
          
TripInfo1 <- dboTripInfo %>% 
  filter(substring(TripID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "COLL") %>%
  arrange(TripID)

SampleEvent1 <- dboSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber)

SampleEventWQ1 <- dboSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventWQID, 19, 22)) %>%
  filter(substring(SampleEventWQID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEventWQ1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, SampleEventWQID)

#Get all CI data to check data status, then limit to proofed data for datachecks
CI_t <- dboCI %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL") %>%
  left_join(FixedLocations1, CI1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)
CI1 <- CI_t %>% filter(DataStatus == "Proofed")

#Get all Dermo data to check data status, then limit to proofed data for datachecks
Dermo_t <- dboDermo %>%
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22),
         DermoMantle = as.numeric(DermoMantle),
         DermoGill = as.numeric(DermoGill)) %>% 
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL") %>%
  left_join(FixedLocations1, Dermo1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)
Dermo1 <- Dermo_t %>% filter(DataStatus == "Proofed")

#Get all Repro data to check data status - don't limit to proofed since Dermo data is checked monthly, Repro checked quarterly
Repro_t <- dboRepro %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>% 
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL") %>%
  left_join(FixedLocations1, Repro1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, OysterID)
Repro1 <- Repro_t

#Combine data types and status with TripInfo
TripInfo2 <- left_join(left_join(left_join(TripInfo1 %>%
  select(TripID, TripDate, DataStatus, Comments) %>% arrange(TripID),
CI_t %>% mutate(TripID = substring(SampleEventID, 1, 17)) %>% subset(TripID %in% TripInfo1$TripID) %>%
  group_by(TripID, DataStatus) %>% summarise(Count = n()) %>% pivot_wider(names_from = DataStatus, names_glue = "C_{DataStatus}", values_from = Count)),
Dermo_t %>% mutate(TripID = substring(SampleEventID, 1, 17)) %>% subset(TripID %in% TripInfo1$TripID) %>%
  group_by(TripID, DataStatus) %>% summarise(Count = n()) %>% pivot_wider(names_from = DataStatus, names_glue = "D_{DataStatus}", values_from = Count)),
Repro_t %>% mutate(TripID = substring(SampleEventID, 1, 17)) %>% subset(TripID %in% TripInfo1$TripID) %>%
  group_by(TripID, DataStatus) %>% summarise(Count = n()) %>% pivot_wider(names_from = DataStatus, names_glue = "R_{DataStatus}", values_from = Count))

#"Historic" data
hsdbTripInfo <- hsdbTripInfo %>% 
  filter(substring(TripID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "COLL")  %>%
  arrange(TripID)

hsdbSampleEvent <- hsdbSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL") %>%
  arrange(TripDate)

hsdbSampleEventWQ <- hsdbSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventWQID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "COLL") %>%
  arrange(TripDate)

hsdbCI <- hsdbCI %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

hsdbDermo <- hsdbDermo %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

hsdbRepro <- hsdbRepro %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) %in% EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  arrange(TripDate)

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the dbo schema
ERR_Table1 <- data.frame()
ERR_Table1a <- data.frame()
ERR_Table1b <- data.frame()
ERR_Table1c <- data.frame()
ERR_Table1d <- data.frame()
ERR_Table1e <- data.frame()
ERR_Table1f <- data.frame()

if (nrow(TripInfo1[duplicated(TripInfo1$TripID), ]) > 0) {
  ERR_Table1a <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "TripInfo", TripInfo1[duplicated(TripInfo1$TripID), ])) %>% 
    mutate(PrimaryKey = TripID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEvent1[duplicated(SampleEvent1$SampleEventID), ]) > 0) {
  ERR_Table1b <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEvent", SampleEvent1[duplicated(SampleEvent1$SampleEventID), ])) %>% 
    mutate(PrimaryKey = SampleEventID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ]) > 0) {
  ERR_Table1c <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEventWQ", SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ])) %>% 
    mutate(PrimaryKey = SampleEventWQID) %>% 
    select(schema, Table, PrimaryKey)
}

if (nrow(CI1[duplicated(CI1$OysterID), ]) > 0) {
  ERR_Table1d <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "ConditionIndex", CI1[duplicated(CI1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(Dermo1[duplicated(Dermo1$OysterID), ]) > 0) {
  ERR_Table1e <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "Dermo", Dermo1[duplicated(Dermo1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(Repro1[duplicated(Repro1$OysterID), ]) > 0) {
  ERR_Table1f <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "Repro", Repro1[duplicated(Repro1$OysterID), ])) %>% 
    mutate(PrimaryKey = OysterID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Tablex <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, CI1$OysterID, Dermo1$OysterID, Repro1$OysterID)
dest <- list(hsdbTripInfo$TripID, hsdbSampleEvent$SampleEventID, hsdbSampleEventWQ$SampleEventWQID, hsdbCI$OysterID, hsdbDermo$OysterID, hsdbRepro$OysterID)
tabl <- list("TripInfo", "SampleEvent", "SampleEventWQ", "ConditionIndex", "Dermo", "Repro")

# Loop through values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if ((check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Tablex <- rbind(ERR_Tablex, data.frame(schema = "hsdb", Table = tabl[[i]], PrimaryKey = check_id))
    }
  }
}

ERR_Table1 <- rbind(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Table1f, ERR_Tablex)
rm(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Table1f, ERR_Tablex)


### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, CI1$SampleEventID, Dermo1$SampleEventID, Repro1$SampleEventID)
dest <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ", "ConditionIndex", "Dermo", "Repro")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if (!(check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless
ERR_Table3 <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
dest <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, CI1$SampleEventID, Dermo1$SampleEventID, Repro1$SampleEventID)
tabl <- list("TripInfo", "SampleEvent&WQ", "SampleEvent&CI", "SampleEvent&Dermo", "SampleEvent&Repro")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
    if (!(check_id %in% dest[[i]])) {
      ERR_Table3 <- rbind(ERR_Table3, data.frame(Table = tabl[[i]], ChildlessPrimaryKey = check_id))
    }
  }
}
ERR_Table3 <- if(length(ERR_Table3) > 0){distinct(ERR_Table3) %>% mutate(Table = gsub("^SampleEvent&", "", Table)) %>% table() %>% as.data.frame() %>% pivot_wider(id_cols = ChildlessPrimaryKey, names_from = Table, values_from = Freq)} else {data.frame()}

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly
ERR_Table4 <- data.frame()
pkid <- list(SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID)
fkid <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ")
numb <- list(17, 24)

for (i in seq_along(pkid)) {
  for (j in seq_along(fkid[[i]])) {
    check_fkid <- fkid[[i]][j]
    check_pkid <- substring(pkid[[i]][j],1,numb[[i]])
    if (check_fkid != check_pkid) {
      ERR_Table4 <- rbind(ERR_Table4, data.frame(Table = tabl[[i]], PrimaryKey = pkid[[i]][j], ForeignKey = check_fkid))
    }
  }
}

# Ensure that Primary Keys and Foreign Keys have been formed correctly for OysterID in CI, Dermo, and Repro
ERR_Table4a <- CI1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "C", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

ERR_Table4b <- Dermo1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "D", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

ERR_Table4c <- Repro1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "D", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
TripInfo_nulls <- filter(TripInfo1, is.na(TripID) | is.na(TripType) | is.na(TripDate) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(TripID, TripDate, TripType, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEvent_nulls <- filter(SampleEvent1, is.na(SampleEventID) | is.na(TripID) | is.na(FixedLocationID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed)) %>%
  select(SampleEventID, TripID, FixedLocationID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEventWQ_nulls <- filter(SampleEventWQ1, is.na(SampleEventWQID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventWQID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

ConditionIndex_nulls <- filter(CI1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

Dermo_nulls <- filter(Dermo1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

Repro_nulls <- filter(Repro1, is.na(OysterID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(OysterID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

# Remove unneeded data frames and values

rm(dboFixedLocations, dboRepro, dboDermo, dboCI, dboSampleEvent, dboSampleEventWQ, dboTripInfo, dest, FixedLocations1, hsdbRepro, hsdbDermo, hsdbCI, hsdbSampleEvent, hsdbSampleEventWQ, hsdbTripInfo, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table3) > 0 | nrow(ERR_Table4) > 0 | nrow(ERR_Table4a) > 0 | nrow(ERR_Table4b) > 0 | nrow(ERR_Table4c) > 0 | nrow(TripInfo_nulls) > 0 | nrow(SampleEvent_nulls) > 0 | nrow(SampleEventWQ_nulls) > 0 | nrow(ConditionIndex_nulls) > 0 | nrow(Dermo_nulls) > 0 | nrow(Repro_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## TripInfo #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## SampleEvent #
  # Unexpected Null values
null_SampleEvents <- filter(SampleEvent1, is.na(FixedLon) & (is.na(LatitudeDec) | is.na(LongitudeDec) | is.na(LatDec) | is.na(LatMin) | is.na(LongDec) | is.na(LongMin))) %>%
  select(SampleEventID, LatitudeDec, LongitudeDec, LatDec, LatMin, LongDec, LongMin, FixedLon, FixedLat, Comments)

  # Out of range values - not needed for St Pete data currently since station locations are fixed or checked in MGID checks.
SampleEvent_range <- NULL
# Flags SampleEvents that occur over 125 meters (1 nautical mile) from the assigned FixedLocation.  
#SampleEvent1 %>% rowwise() %>% mutate(DistFromFixed = distVincentySphere(c(LongitudeDec, LatitudeDec), c(FixedLon, FixedLat))) %>%
#  filter(DistFromFixed > 1852) %>% select(SampleEventID, LatitudeDec, LongitudeDec, FixedLat, FixedLon, DistFromFixed, Comments)
  
## Water Quality #
  # Unexpected Null values
null_WQs <- filter(SampleEventWQ1, is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(Depth) | is.na(SampleDepth) | is.na(PercentDissolvedOxygen)) %>%
    filter(!grepl(paste(c("ame as", "ame WQ", "ame Water", "ame water"), collapse = '|'), Comments)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Temperature, Salinity, DissolvedOxygen, PercentDissolvedOxygen, pH, Comments)

  # Out of range values
Temp_range <- filter(SampleEventWQ1, Temperature < 10 | Temperature > 34) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Temperature, Comments)
Sal_range <- filter(SampleEventWQ1, Salinity < 0.5 | Salinity > 38) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Salinity, Comments)
DO_range <- SampleEventWQ1 %>% 
  mutate(DO.Sat = DO.saturation(DO.mgl = DissolvedOxygen, temp.C = Temperature, elevation.m = 0, salinity = Salinity)) %>%
  filter(DO.Sat < 0.50 | DO.Sat > 1.50) %>%
  mutate(DO.Sat = percent(DO.Sat, accuracy = 1)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, PercentDissolvedOxygen,  DO.Sat, Comments)
DOPct_range <- SampleEventWQ1 %>% 
  filter(PercentDissolvedOxygen < 20 | PercentDissolvedOxygen > 150) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, PercentDissolvedOxygen, Comments)
pH_range <- filter(SampleEventWQ1, pH < 7.0 | pH > 8.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, pH, Comments)
Depth_range <- filter(SampleEventWQ1, Depth < 0 | Depth > 3.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
SampleDepth_range <- filter(SampleEventWQ1, SampleDepth < 0 | SampleDepth > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
Secchi_range <- filter(SampleEventWQ1, Secchi < 0 | Secchi > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Secchi, Comments)
TurbidityYSI_range <- filter(SampleEventWQ1, TurbidityYSI < -2 | TurbidityYSI > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityYSI, Comments)
TurbidityHach_range <- filter(SampleEventWQ1, TurbidityHach < -2 | TurbidityHach > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityHach, Comments)

## ConditionIndex #
  # Unexpected Null values
null_CI1 <- filter(CI1, is.na(ShellHeight) | is.na(ShellLength) | is.na(ShellWidth) | is.na(TotalWeight)) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, Comments)

null_CI2 <- filter(CI1, is.na(TarePanWeight) | is.na(TissueWetWeight) | is.na(ShellWetWeight) | is.na(TissueDryWeight) | is.na(ShellDryWeight)) %>%
  select(OysterID, TarePanWeight, TissueWetWeight, ShellWetWeight, TissueDryWeight, ShellDryWeight, Comments)

  # Out of range values
CI_range1 <- CI1 %>%
  mutate(
    ErrorCode = case_when(
      ShellHeight < 10 | ShellHeight > 150 ~ "A",
      TRUE ~ NA_character_),
    ErrorCode = case_when(
      ShellLength < 20 | ShellLength > 90 | ShellLength > ShellHeight ~ paste(ErrorCode, "B"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      ShellWidth < 8 | ShellWidth > 50 | ShellWidth > ShellLength ~ paste(ErrorCode, "C"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      TotalWeight < 10 | TotalWeight > 250 ~ paste(ErrorCode, "D"),
      TRUE ~ ErrorCode)) %>%
  filter(!is.na(ErrorCode)) %>%
  mutate(ErrorCode = sub("NA ", "", ErrorCode)) %>%
  select(OysterID, ShellHeight, ShellLength, ShellWidth, TotalWeight, ErrorCode, Comments)
CI_range1caption <- "Out of range Condition data. Comment required for out of range values. <br>(A)Expected range for ShellHeight is 10 to 150 mm. <br>(B)Expected range for ShellLength is 20 to 90 mm and is less than ShellHeight. <br>(C)Expected range for ShellWidth is 8 to 50 mm and is less than ShellLength. <br>(D)Expected range for TotalWeight is 10 to 250 g."

CI_range2 <- CI1 %>%
  mutate(
    ErrorCode = case_when(
      TotalWeight < (TissueWetWeight + ShellWetWeight - TarePanWeight) | (TotalWeight * 0.8) > (TissueWetWeight + ShellWetWeight - TarePanWeight) ~ "A",
      TRUE ~ NA_character_),
    ErrorCode = case_when(
      TarePanWeight < 0.9 | TarePanWeight > 5 ~ paste(ErrorCode, "B"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      TissueWetWeight < ((TotalWeight + TarePanWeight) * 0.05) | TissueWetWeight > 
        ((TotalWeight + TarePanWeight) * 0.4) ~ paste(ErrorCode, "C"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      ShellWetWeight < (TotalWeight * 0.60) | ShellWetWeight > (TotalWeight * 0.99) ~ paste(ErrorCode, "D"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      TissueDryWeight < TarePanWeight | TissueDryWeight > (TissueWetWeight * 0.9) ~ paste(ErrorCode, "E"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      ShellDryWeight < (ShellWetWeight * 0.8) | ShellDryWeight > ShellWetWeight ~ paste(ErrorCode, "F"),
      TRUE ~ ErrorCode)) %>%
  filter(!is.na(ErrorCode)) %>%
  mutate(ErrorCode = sub("NA ", "", ErrorCode)) %>%
  rename(TotalWt = TotalWeight, TarePanWt = TarePanWeight, TissueWetWt = TissueWetWeight, ShellWetWt = ShellWetWeight, TissueDryWt = TissueDryWeight, ShellDryWt = ShellDryWeight) %>%
  select(OysterID, TotalWt, TarePanWt, TissueWetWt, ShellWetWt, TissueDryWt, ShellDryWt, ErrorCode, Comments) %>% arrange(OysterID)
CI_range2caption <- "Out of range Condition data. Comment required for out of range values. <br>(A) Expected range for TotalWeight is 80% to 100% of the sum of TissueWetWeight and ShellWetWeight minus TarePanWeight. <br>(B) Expected range for TarePanWeight is 0.9 to 5.0 g. <br>(C) Expected range for TissueWetWeight is 5% to 40% of the sum of TotalWeight and TarePanWeight. <br>(D) Expected range for ShellWetWeight is 60% to 99% of TotalWeight. <br>(E) Expected range for TissueDryWeight is greater than TarePanWeight and up to 90% of TissueWetWeight. <br>(F) Expected range for ShellDryWeight is 80% to 100% of ShellWetWeight."

## Dermo #
  # Unexpected Null values
null_Dermo <- filter(Dermo1, is.na(ShellHeight) | is.na(TotalWeight) | is.na(ShellWetWeight) | is.na(DermoMantle) | is.na(DermoGill)) %>%
  select(OysterID, ShellHeight, TotalWeight, ShellWetWeight, DermoMantle, DermoGill, Comments)

  # Out of range values
Dermo_range <- Dermo1 %>%
  mutate(
    ErrorCode = case_when(
      ShellHeight < 10 | ShellHeight > 150 ~ "A",
      TRUE ~ NA_character_),
    ErrorCode = case_when(
      TotalWeight < 6 | TotalWeight > 250 ~ paste(ErrorCode, "D"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      ShellWetWeight < (TotalWeight * 0.60) | ShellWetWeight > (TotalWeight * 0.99) ~ paste(ErrorCode, "E"),
      TRUE ~ ErrorCode),
    ErrorCode = case_when(
      DermoMantle < 0 | DermoMantle > 5 | DermoGill < 0 | DermoGill > 5 ~ paste(ErrorCode, "F"),
      TRUE ~ ErrorCode)) %>%
  filter(!is.na(ErrorCode)) %>%
  mutate(ErrorCode = sub("NA ", "", ErrorCode)) %>%
  rename(Height = ShellHeight, Length = ShellLength, Width = ShellWidth, TotalWt = TotalWeight, ShellWetWt = ShellWetWeight, ERR = ErrorCode) %>%
  select(OysterID, Height, Length, Width, TotalWt, ShellWetWt, DermoMantle, DermoGill, ERR, Comments)

Dermo_rangecaption <- "Out of range Dermo data. Comment required for out of range values. <br>(A)Expected range for ShellHeight is 10 to 150 mm. <br>(D)Expected range for TotalWeight is 6 to 250 g. <br>(E)Expected range for ShellWetWeight is 60% to 99% of TotalWeight.  <br>(F)Expected ranges for DermoMantle and DermoGill is 0 to 5."

## Repro #
  # Unexpected Null values
null_Repro <- filter(Repro1, is.na(Sex) | is.na(Parasite) | is.na(BadSlide)) %>%
  select(OysterID, Sex, ReproStage, Parasite, BadSlide, Comments)

  # Out of range values
Repro_range <- Repro1 %>%
  filter((Sex == "M/F" & ReproStage != "Z") | (Parasite == "Buceph" & ReproStage != "Z") | (ReproStage == 4 & Sex != "Z")) %>%
  select(OysterID, Sex, ReproStage, Parasite, BadSlide, Comments)

## Set error messages #

if (nrow(null_SampleEvents) > 0) {
  Mess_null_SampleEvents = ""
} else {
  Mess_null_SampleEvents = "Congratulations! No unexpected null values detected."
}
  
if (nrow(null_WQs) > 0) {
  Mess_null_WQs = ""
} else {
  Mess_null_WQs = "Congratulations! No unexpected null values detected."
}

if (nrow(null_CI1) > 0 | nrow(null_CI2) > 0 ) {
  Mess_null_CI = ""
} else {
  Mess_null_CI = "Congratulations! No unexpected null values detected."
}

if (nrow(null_Dermo) > 0) {
  Mess_null_Dermo = ""
} else {
  Mess_null_Dermo = "Congratulations! No unexpected null values detected."
}

if (nrow(null_Repro) > 0) {
  Mess_null_Repro = ""
} else {
  Mess_null_Repro = "Congratulations! No unexpected null values detected."
}

if (length(SampleEvent_range) == 0) {
  MessSampleEvent_ranges = ""
} else {
  MessSampleEvent_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Temp_range) > 0 | nrow(Sal_range) > 0 | nrow(DO_range) > 0 | nrow(pH_range) > 0 | nrow(Depth_range) > 0 | nrow(SampleDepth_range) > 0 | nrow(Secchi_range) > 0 | nrow(TurbidityYSI_range) > 0 | nrow(TurbidityHach_range)) {
  MessWQ_ranges = ""
} else {
  MessWQ_ranges = "Congratulations! No out of range values detected."
}

if (nrow(CI_range1) > 0 | nrow(CI_range2) > 0) {
  MessCI_ranges = ""
} else {
  MessCI_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Dermo_range) > 0) {
  MessDermo_ranges = ""
} else {
  MessDermo_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Repro_range) > 0) {
  MessRepro_ranges = ""
} else {
  MessRepro_ranges = "Congratulations! No out of range values detected."
}

#List of stored procedure lines
for(i in list(EstuaryCode)) {
  checks <- NULL
  checks[i] <- paste0("EXECUTE [dbo].[spChecksCollections] @CheckStart = &apos;", CheckStart, "&apos;, @CheckEnd = &apos;", CheckEnd, "&apos;, @EstuaryCode = &apos;", i, "&apos;, @DataManager = &apos;", DataManager, "&apos;;")
  }
```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
from the site(s) <p2> `r EstuaryCode` </p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d-%B-%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2,  longtable = TRUE, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! SampleEvents must have 15 child records unless a valid comment is present. *Primary keys will be Childless until data is proofed. Primary keys will also be Childless if an unfinsihed trip is present and no data is entered (i.e. dermo entered, no CI collected).*")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4a) > 0) {kable(ERR_Table4a, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4b) > 0) {kable(ERR_Table4b, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4c) > 0) {kable(ERR_Table4c, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. Status of collection trips. Trips will not show as proofed unless data is entered/proofed and trip is finished.")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "WQ Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(ConditionIndex_nulls) > 0) {kable(ConditionIndex_nulls, caption = "CI Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Dermo_nulls) > 0) {kable(Dermo_nulls, caption = "Dermo Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Repro_nulls) > 0) {kable(Repro_nulls, caption = "Repro Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Sample Event ---</h4>

<p2>`r Mess_null_SampleEvents`</p2>

`r if (nrow(null_SampleEvents) > 0) {kable(null_SampleEvents, caption = "Null Sample Event Data. Comment Required for all Null values")}`

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment Required for all Null values")}`

<h4>--- Condition Index ---</h4>

<p2>`r Mess_null_CI`</p2>

`r if (nrow(null_CI1) > 0) {kable(null_CI1, caption = "Null Condition Index Data. Comment Required for all Null values")}`

`r if (nrow(null_CI2) > 0) {kable(null_CI2, caption = "Null Condition Index Data. Comment Required for all Null values")}`

<h4>--- Dermo ---</h4>

<p2>`r Mess_null_Dermo`</p2>

`r if (nrow(null_Dermo) > 0) {kable(null_Dermo, caption = "Null Dermo Data. Comment Required for all Null values")}`

<h4>--- Repro ---</h4>

<p2>`r Mess_null_Repro`</p2>

`r if (nrow(null_Repro) > 0) {kable(null_Repro, caption = "Null Repro Data. Comment Required for all Null values")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.

<h4>--- Sample Event ---</h4>

<p2>`r MessSampleEvent_ranges`</p2>

`r if (length(SampleEvent_range) == 0) {kable(SampleEvent_range, caption = "If distance from Fixed Location needs to be checked, update code for SampleEvent_range.")}`
`r if (length(SampleEvent_range) > 0) {kable(SampleEvent_range, caption = "Out of range distance from Fixed Location. Expected range is 125 meters. Comment required for out of range values.")}`

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 34.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 35.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range dissolved oxygen data. Expected range is 50% to 120% saturation. . Comment required for out of range values.")}`

`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Condition Index ---</h4>

<p2>`r MessCI_ranges`</p2>

`r if (nrow(CI_range1) > 0) {kable(CI_range1, caption = CI_range1caption)}`

`r if (nrow(CI_range2) > 0) {kable(CI_range2, caption = CI_range2caption)}`

<h4>--- Dermo ---</h4>

<p2>`r MessDermo_ranges`</p2>

`r if (nrow(Dermo_range) > 0) {kable(Dermo_range, caption = Dermo_rangecaption)}`

<h4>--- Repro ---</h4>

<p2>`r MessRepro_ranges`</p2>

`r if (nrow(Repro_range) > 0) {kable(Repro_range, caption = "Out of range Repro data. If Sex = M/F, ReproStage MUST = Z. If Parasite = Buceph, ReproStage MUST = Z. If ReproStage = 4, Sex MUST = Z.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

`r paste(checks, collapse = "<br>")`

`r knit_exit()`

```{sql SQL code, eval=FALSE, include=FALSE}
--- This code creates a stored procedure in the database. 
-- To do so, copy and paste this code VERBATIM into SSMS
-- DO NOT RUN THIS CODE WITH R --

CREATE PROCEDURE [dbo].[spChecksCollections](
	@CheckStart AS DATE,
	@CheckEnd AS DATE,
	@EstuaryCode AS VARCHAR(2),
	@DataManager AS VARCHAR(max)
	)
AS
BEGIN
	DECLARE @CompletedDate DATE;
	SET @CompletedDate = cast(getDate() as date);

	IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
	BEGIN
    DROP TABLE #ValidTrips;
  END

	CREATE TABLE #ValidTrips (
		TripID VARCHAR(50)
	);

	INSERT INTO #ValidTrips (TripID)
	SELECT TripID
	FROM dbo.TripInfo
	WHERE TripDate >= @CheckStart AND TripDate <= @CheckEnd
	AND DataStatus = 'Proofed' AND TripID like CONCAT(@EstuaryCode, 'COLL%');

	-- Query the TripInfo table using the temporary table
	UPDATE dbo.TripInfo 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEvent table using the temporary table
	UPDATE dbo.SampleEvent 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEventWQ table using the temporary table
	UPDATE dbo.SampleEventWQ 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

  -- Query the ConditionIndex table using the temporary table
  UPDATE dbo.ConditionIndex 
  SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
  WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));
  
  -- Query the Dermo table using the temporary table
  UPDATE dbo.Dermo 
  SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
  WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));
  
  -- Query the Repro table using the temporary table
  UPDATE dbo.Repro 
  SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
  WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

  -- Insert the Completed data into hsdb, and DELETE FROM dbo
  INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.ConditionIndex 
  (OysterID, SampleEventID, ShellHeight, ShellLength, ShellWidth, TotalWeight, TarePanWeight, TissueWetWeight, ShellWetWeight, TissueDryWeight, ShellDryWeight, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments, AdminNotes)
  SELECT 
  OysterID, SampleEventID, ShellHeight, ShellLength, ShellWidth, TotalWeight, TarePanWeight, TissueWetWeight, ShellWetWeight, TissueDryWeight, ShellDryWeight, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments, AdminNotes
  FROM ConditionIndex WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.ConditionIndex WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.Dermo 
  (OysterID, SampleEventID, ShellHeight, ShellLength, ShellWidth, TotalWeight, ShellWetWeight, DermoMantle, DermoGill, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments,	AdminNotes)
  SELECT 
  OysterID, SampleEventID, ShellHeight, ShellLength, ShellWidth, TotalWeight, ShellWetWeight, DermoMantle, DermoGill, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments, AdminNotes
  FROM Dermo WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.Dermo WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.Repro 
  (OysterID, SampleEventID, Sex, ReproStage, Parasite, BadSlide, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments, AdminNotes)
  SELECT OysterID, SampleEventID, Sex, ReproStage, Parasite, BadSlide, DataStatus, DateEntered, EnteredBy, DateProofed, ProofedBy, DateCompleted, CompletedBy, Comments, AdminNotes
  FROM Repro WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.Repro WHERE DataStatus = 'Completed';
  
END

```
