---
title: "Collections Data Checks"
subtitle: "Shell Pest"
output:
  html_document:
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2017-01-01")  # Start Date for Checks
CheckEnd <- as.Date("2017-08-28")  # End Date for Checks
EstuaryCode = "AB"  # Estuary Code. Use 2-letter code in Primary Keys
DataManager = "Matthew Davis"
Database = "OysterLocalMD20231019"
```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
#library(rMR) DO saturation calculation
library(scales) # Not sure if this library is needed or not
#library(geosphere) SampleEvent distance calculations
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 8pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 18pt;
font-weight: bold;
}

h2 {
font-size: 14pt;
font-weight: bold;
}

h3 {
font-size: 12pt;
font-style: italic;
}

h4 {
font-size: 10pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = "localhost\\MATTLOCALSQL",
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == EstuaryCode)

hsdbCI <- tbl(con,in_schema("hsdb", "ConditionIndex")) %>%
  mutate(DataStatus = "Completed") %>% # For teting only, remove line when done testing
  collect() 

hsdbShellPest <- tbl(con,in_schema("hsdb", "ShellPest")) %>%
  collect() 

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Collections trips in the specified Estuary, in the correct date range, which have been Proofed, are present.ShellPest data MUST be done AFTER ConditionIndex checks are performed
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  select(FixedLocationID, Estuary, SectionName, StationNumber) %>% 
  distinct()
          
hsdbCI <- hsdbCI %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Completed") %>%
  arrange(TripDate)

ShellPest1 <- hsdbShellPest %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "COLL" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, ShellPest1, by = c("FixedLocationID")) %>%
  arrange(TripDate)

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Table1 <- data.frame()

if (nrow(ShellPest1[duplicated(ShellPest1$ShellPestID), ]) > 0) {
  ERR_Table1 <- bind_rows(data.frame(schema = "hsdb", Table = "ShellPest", ShellPest1[duplicated(ShellPest1$ShellPestID), ])) %>% 
    mutate(PrimaryKey = ShellPestID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(ShellPest1$OysterID, ShellPest1$SampleEventID, hsdbCI$OysterID)
dest <- list(hsdbCI$OysterID, hsdbCI$SampleEventID, ShellPest1$OysterID)
tabl <- list("ShellPest", "SampleEvent", "ConditionIndex")

# Loop through ShellPest1$OysterID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the id exists in hsdbCI$OysterID
    if (!(check_id %in% dest[[i]])) {
    # Add id to ERR_Table if it is missing
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless. Not needed, no child records for ShellPest
#ERR_Table3 <- data.frame()

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly for OysterID in ShellPest
ERR_Table4 <- ShellPest1 %>%
  mutate(ExpectedPK = paste0(Estuary, SectionName, "C", substr(year(TripDate), 3, 4), format(TripDate, "%m"), "-", substr(OysterID, 10, 11))) %>%
  filter(OysterID != ExpectedPK) %>%
  select(PrimaryKey = "OysterID", SampleEventID, ExpectedPK)

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
ShellPest_nulls <- filter(ShellPest1, is.na(ShellPestID), is.na(OysterID) | is.na(SampleEventID) | is.na(PhotoSurface) | is.na(DateProcessed) | is.na(ProcessedBy) | is.na(OldSampleNumber) ) %>%
  select(ShellPestID, OysterID, SampleEventID, PhotoSurface, DateProcessed, ProcessedBy, OldSampleNumber, Comments)

# Remove unneeded data frames and values

#rm(dboFixedLocations, dest, FixedLocations1, hsdbCI, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table4) > 0 | nrow(ShellPest_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## ShellPest #
  # Unexpected Null values
null_ShellPest <- filter(ShellPest1, is.na(TotalArea), is.na(TotalHeight), is.na(TotalLength), is.na(ClionaArea), is.na(PolydoraArea), is.na(ClamCount), is.na(ClamAverageDiameter)) %>%
  select(ShellPestID, TotalArea, TotalHeight, TotalLength, ClionaArea, PolydoraArea, ClamCount, ClamAverageDiameter, Comments)

  # Out of range values
ShellPest2 <- right_join(hsdbCI, ShellPest1, by = c("OysterID")) %>%
  select(ShellPestID, OysterID,SampleEventID.x, ShellHeight, ShellLength, OldSampleNumber.x, PhotoSurface, TotalArea, TotalHeight, TotalLength, ClionaArea, PolydoraArea, ClamCount, ClamAverageDiameter, Comments.y) %>%
  mutate(MaxArea = ShellHeight * ShellLength)
ShellPest_range1 <- filter(ShellPest2, 
                           TotalArea < MaxArea * 0.5 | TotalArea > MaxArea * 0.9 | 
                             TotalHeight < ShellHeight * 0.6 | TotalHeight > ShellHeight * 1.4 |
                             TotalLength < ShellLength * 0.6 | TotalLength > ShellLength * 1.4) %>%
  select(ShellPestID, OysterID, ShellHeight, TotalHeight, ShellLength, TotalLength, TotalArea, MaxArea, Comments.y) 
ShellPest_range2 <- filter(ShellPest2, 
                           ClionaArea < 0 | ClionaArea > TotalArea * 0.95 | 
                             PolydoraArea < 0 | PolydoraArea > TotalArea * 0.95 | 
                             ClamCount < 0 | ClamCount > 10 | 
                             ClamAverageDiameter < 0 | ClamAverageDiameter > 6) %>%
  select(ShellPestID, OysterID, TotalArea, ClionaArea, PolydoraArea, ClamCount, ClamAverageDiameter, Comments.y)

## Set error messages #

if (nrow(null_ShellPest) > 0) {
  Mess_null_ShellPest = ""
} else {
  Mess_null_ShellPest = "Congratulations! No unexpected null values detected."
}

if (nrow(ShellPest_range1) > 0 | nrow(ShellPest_range2) > 0) {
  MessShellPest_ranges = ""
} else {
  MessShellPest_ranges = "Congratulations! No out of range values detected."
}

```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d.%B.%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! SampleEvents must have 15 child records unless a valid comment is present.")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4a) > 0) {kable(ERR_Table4a, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4b) > 0) {kable(ERR_Table4b, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(ERR_Table4c) > 0) {kable(ERR_Table4c, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(ConditionIndex_nulls) > 0) {kable(ConditionIndex_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Dermo_nulls) > 0) {kable(Dermo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Repro_nulls) > 0) {kable(Repro_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Sample Event ---</h4>

<p2>`r Mess_null_SampleEvents`</p2>

`r if (nrow(null_SampleEvents) > 0) {kable(null_SampleEvents, caption = "Null Sample Event Data. Comment Required for all Null values")}`

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment Required for all Null values")}`

<h4>--- Condition Index ---</h4>

<p2>`r Mess_null_CI`</p2>

`r if (nrow(null_CI) > 0) {kable(null_CI, caption = "Null Condition Index Data. Comment Required for all Null values")}`

<h4>--- Dermo ---</h4>

<p2>`r Mess_null_Dermo`</p2>

`r if (nrow(null_Dermo) > 0) {kable(null_Dermo, caption = "Null Dermo Data. Comment Required for all Null values")}`

<h4>--- Repro ---</h4>

<p2>`r Mess_null_Repro`</p2>

`r if (nrow(null_Repro) > 0) {kable(null_Repro, caption = "Null Repro Data. Comment Required for all Null values")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.

<h4>--- Sample Event ---</h4>

<p2>`r MessSampleEvent_ranges`</p2>

`r if (nrow(SampleEvent_range) > 0) {kable(SampleEvent_range, caption = "Out of range distance from Fixed Location. Expected range is 1,852 meters (1 nautical mile). Comment required for out of range values.")}`

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 33.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 35.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range dissolved oxygen data. Expected range is 50% to 120% saturation. . Comment required for out of range values.")}`

`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Condition Index ---</h4>

<p2>`r MessCI_ranges`</p2>

`r if (nrow(CI_range1) > 0) {kable(CI_range1, caption = "Out of range Condition data. Expected range for ShellHeight is 10 to 150 mm. Expected range for ShellLength is 20 to 90 mm and is less than ShellHeight. Expected range for ShellWidth is 8 to 50 mm and is less than ShellLength. Expected range for TotalWeight is 10 to 250 g. Comment required for out of range values.")}`

`r if (nrow(CI_range2) > 0) {kable(CI_range2, caption = "Out of range Condition data. Expected range for TarePanWeight is 0.9 to 5.0 g. Expected range for TissueWetWeight is 5% to 40% of the sum of TotalWeight and TarePanWeight. Expected range for ShellWetWeight is 50% to 99% of TotalWeight. Expected range for TissueDryWeight is greater than TarePanWeight and up to 90% of TissueWetWeight. Expected range for ShellDryWeight is 80% to 100% of ShellWetWeight. Comment required for out of range values.")}`

<h4>--- Dermo ---</h4>

<p2>`r MessDermo_ranges`</p2>

`r if (nrow(Dermo_range) > 0) {kable(Dermo_range, caption = "Out of range Dermo data. Expected range for ShellHeight is 10 to 150 mm. Expected range for ShellLength is 20 to 90 mm and is less than ShellHeight. Expected range for ShellWidth is 8 to 50 mm and is less than ShellLength. Expected range for TotalWeight is 10 to 250 g. Expected ranges for DermoMantle and DermoGill is 0 to 5. Comment required for out of range values.")}`

<h4>--- Repro ---</h4>

<p2>`r MessRepro_ranges`</p2>

`r if (nrow(Repro_range) > 0) {kable(Repro_range, caption = "Out of range Repro data. If Sex = M/F, ReproStage MUST be Null. If Parasite = Buceph, ReproStage MUST be Null. If ReproStage = 4, Sex MUST = Z.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

\~\~\~\~ Note to self: The bulk of this code may be better as a Stored
Procedure. Then the SQL Code here would be:\
EXEC sp_CompleteCollections \'`r EstuaryCode`\', \'`r CheckStart`\',
\'`r CheckEnd`\', \'`r DataManager`\';

\~\~\~\~ SQL code with comments in un-run chunk at end.

\~\~\~\~ End note

IF OBJECT_ID(\'tempdb..#ValidTrips\') IS NOT NULL BEGIN DROP TABLE
#ValidTrips; END

CREATE TABLE #ValidTrips ( TripID VARCHAR(50) );

INSERT INTO #ValidTrips (TripID) SELECT TripID FROM TripInfo WHERE
TripDate \> \'`r CheckStart`\' AND TripDate \< \'`r CheckEnd`\' AND
DataStatus = \'Proofed\' AND TripID like \'`r EstuaryCode`SRVY%\';

UPDATE TripInfo SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

UPDATE SampleEvent SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d.%B.%Y")`\'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

UPDATE SampleEventWQ SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

UPDATE ConditionIndex SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

UPDATE Dermo SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

UPDATE Repro SET DataStatus = \'Completed\', CompletedBy =
\'`r DataManager`\', DateCompleted = \'`r format(Sys.Date(), "%d-%B-%Y")`\'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE
TripID IN (SELECT TripID FROM #ValidTrips));

INSERT INTO hsdb.TripInfo SELECT \* FROM TripInfo WHERE DataStatus =
\'Completed\';

DELETE FROM dbo.TripInfo WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SampleEvent SELECT \* FROM SampleEvent WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.SampleEvent WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.SampleEventWQ SELECT \* FROM SampleEventWQ WHERE
DataStatus = \'Completed\';

DELETE FROM dbo.SampleEventWQ WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.ConditionIndex SELECT \* FROM ConditionIndex WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.ConditionIndex WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.Dermo SELECT \* FROM Dermo WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.Dermo WHERE DataStatus = \'Completed\';

INSERT INTO hsdb.Repro SELECT \* FROM Repro WHERE DataStatus
= \'Completed\';

DELETE FROM dbo.Repro WHERE DataStatus = \'Completed\';

`r knit_exit()`

```{sql SQL code, eval=FALSE, include=FALSE}

-- Check that there is not already a temporary table to store valid TripIDs. If there is, DELETE it and create a clean temporary table
IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
BEGIN
    DROP TABLE #ValidTrips;
END

CREATE TABLE #ValidTrips (
    TripID VARCHAR(50)
);

INSERT INTO #ValidTrips (TripID)
SELECT TripID
FROM TripInfo
WHERE TripDate > '`r CheckStart`' AND TripDate < '`r CheckEnd`'
AND DataStatus = 'Proofed' AND TripID like '`r EstuaryCode`SRVY%';

-- Query the TripInfo table using the temporary table
UPDATE TripInfo 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

-- Query the SampleEvent table using the temporary table
UPDATE SampleEvent 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d.%B.%Y")`'
WHERE TripID IN (SELECT TripID FROM #ValidTrips);

-- Query the SampleEventWQ table using the temporary table
UPDATE SampleEventWQ 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Query the ConditionIndex table using the temporary table
UPDATE ConditionIndex 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Query the Dermo table using the temporary table
UPDATE Dermo 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Query the Repro table using the temporary table
UPDATE Repro 
SET DataStatus = 'Completed', CompletedBy = '`r DataManager`', DateCompleted = '`r format(Sys.Date(), "%d-%B-%Y")`'
WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

-- Insert the Completed data into hsdb, and DELETE FROM dbo
INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';

DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';

DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';

INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';

DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';

INSERT INTO hsdb.ConditionIndex SELECT * FROM ConditionIndex WHERE DataStatus = 'Completed';

DELETE FROM dbo.ConditionIndex WHERE DataStatus = 'Completed';

INSERT INTO hsdb.Dermo SELECT * FROM Dermo WHERE DataStatus = 'Completed';

DELETE FROM dbo.Dermo WHERE DataStatus = 'Completed';

INSERT INTO hsdb.Repro SELECT * FROM Repro WHERE DataStatus = 'Completed';

DELETE FROM dbo.Repro WHERE DataStatus = 'Completed';

```
