---
title: "Survey Data Checks"
output:
  html_document:
knit: (function(inputFile, encoding) {rmarkdown::render(input = inputFile, encoding = encoding, output_file = paste0(substr(inputFile, 1, nchar(inputFile)-4), "_", Sys.Date(), '.html')) })
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2023-01-01")  # Start Date for Checks
CheckEnd <- as.Date("2024-05-30")  # End Date for Checks
EstuaryCode = "CR"  # Estuary Code. Use 2-letter code in Primary Keys
DataManager = "Erica Levine"
Database = "Oysters_24-05-28_test"
Server = "localhost\\ERICALOCALSQL"
```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(rMR)
library(scales)
library(geosphere)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 8pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 18pt;
font-weight: bold;
}

h2 {
font-size: 14pt;
font-weight: bold;
}

h3 {
font-size: 12pt;
font-style: italic;
}

h4 {
font-size: 10pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = Server,
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == EstuaryCode)

hsdbTripInfo <- tbl(con,in_schema("hsdb", "TripInfo")) %>%
  collect() 

dboTripInfo <- tbl(con,in_schema("dbo", "TripInfo")) %>%
  collect() 
  
hsdbSampleEvent <- tbl(con,in_schema("hsdb", "SampleEvent")) %>%
  collect() 
  
dboSampleEvent <- tbl(con,in_schema("dbo", "SampleEvent")) %>%
  collect() 

hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() 

dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() 

hsdbSurveyQuadrat <- tbl(con,in_schema("hsdb", "SurveyQuadrat")) %>%
  collect() 

dboSurveyQuadrat <- tbl(con,in_schema("dbo", "SurveyQuadrat")) %>%
  collect()

hsdbSurveySH <- tbl(con,in_schema("hsdb", "SurveySH")) %>%
  collect() 

dboSurveySH <- tbl(con,in_schema("dbo", "SurveySH")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Recruitment trips in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber),
         FixedLat = LatitudeDec,
         FixedLon = LongitudeDec) %>% 
  select(FixedLocationID, Estuary, SectionName, StationNumber, FixedLat, FixedLon) %>% 
  distinct()
          
TripInfo1 <- dboTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  arrange(TripID)

TripInfo2 <- TripInfo1 %>%
  select(TripID, TripDate, Comments) %>%
  arrange(TripID)

SampleEvent1 <- dboSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber)

SampleEventWQ1 <- dboSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventWQID, 19, 22)) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEventWQ1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, SampleEventWQID)

SurveyQuadrat1 <- dboSurveyQuadrat %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(QuadratID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SurveyQuadrat1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, QuadratID)

SurveySH1 <- dboSurveySH %>% 
  mutate(TripDate = as.Date(substring(QuadratID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(QuadratID, 19, 22),
         ShellHeight = as.numeric(ShellHeight)) %>% # Datatype in database is varchar due to weird PowerApps bug
  filter(substring(QuadratID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(QuadratID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SurveyQuadrat1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, ShellHeightID)

hsdbTripInfo <- hsdbTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(TripID,3,6) == "SRVY")  %>%
  arrange(TripID)

hsdbSampleEvent <- hsdbSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "SRVY") %>%
  arrange(TripDate)

hsdbSampleEventWQ <- hsdbSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventWQID,3,6) == "SRVY") %>%
  arrange(TripDate)

hsdbSurveyQuadrat <- hsdbSurveyQuadrat %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(QuadratID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(SampleEventID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  arrange(TripDate)

hsdbSurveySH <- hsdbSurveySH %>% 
  mutate(TripDate = as.Date(substring(QuadratID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(QuadratID, 19, 22)) %>%
  filter(substring(QuadratID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate <= CheckEnd & substring(QuadratID,3,6) == "SRVY" & DataStatus == "Proofed") %>%
  arrange(TripDate)

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the dbo schema
ERR_Table1 <- data.frame()
ERR_Table1a <- data.frame()
ERR_Table1b <- data.frame()
ERR_Table1c <- data.frame()
ERR_Table1d <- data.frame()
ERR_Table1e <- data.frame()

if (nrow(TripInfo1[duplicated(TripInfo1$TripID), ]) > 0) {
  ERR_Table1a <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "TripInfo", TripInfo1[duplicated(TripInfo1$TripID), ])) %>% 
    mutate(PrimaryKey = TripID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEvent1[duplicated(SampleEvent1$SampleEventID), ]) > 0) {
  ERR_Table1b <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEvent", SampleEvent1[duplicated(SampleEvent1$SampleEventID), ])) %>% 
    mutate(PrimaryKey = SampleEventID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ]) > 0) {
  ERR_Table1c <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEventWQ", SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ])) %>% 
    mutate(PrimaryKey = SampleEventWQID) %>% 
    select(schema, Table, PrimaryKey)
}

if (nrow(SurveyQuadrat1[duplicated(SurveyQuadrat1$QuadratID), ]) > 0) {
  ERR_Table1d <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SurveyQuadrat", SurveyQuadrat1[duplicated(SurveyQuadrat1$QuadratID), ])) %>% 
    mutate(PrimaryKey = QuadratID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SurveySH1[duplicated(SurveySH1$ShellHeightID), ]) > 0) {
  ERR_Table1e <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SurveySH", SurveySH1[duplicated(SurveySH1$ShellHeightID), ])) %>% 
    mutate(PrimaryKey = ShellHeightID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Tablex <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, SurveyQuadrat1$QuadratID, SurveySH1$ShellHeightID)
dest <- list(hsdbTripInfo$TripID, hsdbSampleEvent$SampleEventID, hsdbSampleEventWQ$SampleEventWQID, hsdbSurveyQuadrat$QuadratID, hsdbSurveySH$ShellHeightID)
tabl <- list("TripInfo", "SampleEvent", "SampleEventWQ", "SurveyQuadrat", "SurveySH")

# Loop through values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if ((check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Tablex <- rbind(ERR_Tablex, data.frame(schema = "hsdb", Table = tabl[[i]], PrimaryKey = check_id))
    }
  }
}

ERR_Table1 <- rbind(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Tablex)
rm(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Table1e, ERR_Tablex)


### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, SurveyQuadrat1$SampleEventID, SurveySH1$QuadratID)
dest <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SurveyQuadrat1$QuadratID)
tabl <- list("SampleEvent", "SampleEventWQ", "SurveyQuadrat", "SurveySH")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if (!(check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless
ERR_Table3 <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID, SurveyQuadrat1$QuadratID)
dest <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, SurveyQuadrat1$SampleEventID, SurveySH1$QuadratID)
tabl <- list("TripInfo", "SampleEvent", "SampleEvent", "SurveyQuadrat")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
    if (!(check_id %in% dest[[i]])) {
      ERR_Table3 <- rbind(ERR_Table3, data.frame(Table = tabl[[i]], ChildlessPrimaryKey = check_id))
    }
  }
}
ERR_Table3 <- distinct(ERR_Table3) 

# Ensure there are 15 quadrats per SampleEvent for all Sites except TB 2023-current
# Counts up the number of quadrats that were made
ERR_Table3a <- if(EstuaryCode == "TB" & CheckStart >= as.Date("2023-01-01")){ as.data.frame(table(SurveyQuadrat1$SampleEventID)) %>% 
    rename("SampleEventID" = "Var1", "NumOfQuads" = "Freq") %>% filter(NumOfQuads != 5) %>%
    merge(SurveyQuadrat1 %>% dplyr::select(SampleEventID, Comments))
} else {as.data.frame(table(SurveyQuadrat1$SampleEventID)) %>% # Counts up the number of quadrats that were made
  rename("SampleEventID" = "Var1", "NumOfQuads" = "Freq") %>% filter(NumOfQuads != 15) %>%
    merge(SurveyQuadrat1 %>% dplyr::select(SampleEventID, Comments))}

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly
ERR_Table4 <- data.frame()
pkid <- list(SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, SurveyQuadrat1$QuadratID, SurveySH1$ShellHeightID)
fkid <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, SurveyQuadrat1$SampleEventID, SurveySH1$QuadratID)
tabl <- list("SampleEvent", "SampleEventWQ", "SurveyQuadrat", "SurveySH")
numb <- list(17, 24, 24, 27)

for (i in seq_along(pkid)) {
  for (j in seq_along(fkid[[i]])) {
    check_fkid <- fkid[[i]][j]
    check_pkid <- substring(pkid[[i]][j],1,numb[[i]])
    if (check_fkid != check_pkid) {
      ERR_Table4 <- rbind(ERR_Table4, data.frame(Table = tabl[[i]], PrimaryKey = pkid[[i]][j], ForeignKey = check_fkid))
    }
  }
}

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
TripInfo_nulls <- filter(TripInfo1, is.na(TripID) | is.na(TripType) | is.na(TripDate) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(TripID, TripDate, TripType, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEvent_nulls <- filter(SampleEvent1, is.na(SampleEventID) | is.na(TripID) | is.na(FixedLocationID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventID, TripID, FixedLocationID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEventWQ_nulls <- filter(SampleEventWQ1, is.na(SampleEventWQID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventWQID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SurveyQuadrat_nulls <- filter(SurveyQuadrat1, is.na(QuadratID) | is.na(SampleEventID) | is.na(QuadratNumber) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(QuadratID, SampleEventID, QuadratNumber, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SurveySH_nulls <- filter(SurveySH1, is.na(QuadratID) | is.na(QuadratID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(ShellHeightID, QuadratID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

# Remove unneeded data frames and values

rm(dboFixedLocations, dboSurveyQuadrat, dboSurveySH, dboSampleEvent, dboSampleEventWQ, dboTripInfo, dest, FixedLocations1, hsdbSurveyQuadrat, hsdbSurveySH, hsdbSampleEvent, hsdbSampleEventWQ, hsdbTripInfo, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table3) > 0 | nrow(ERR_Table3a) > 0 | nrow(ERR_Table4) > 0 | nrow(TripInfo_nulls) > 0 | nrow(SampleEvent_nulls) > 0 | nrow(SampleEventWQ_nulls) > 0 | nrow(SurveyQuadrat_nulls) > 0 | nrow(SurveySH_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## TripInfo #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## SampleEvent #
  # Unexpected Null values
null_SampleEvents <- filter(SampleEvent1, is.na(FixedLon) & (is.na(LatitudeDec) | is.na(LongitudeDec) | is.na(LatDec) | is.na(LatMin) | is.na(LongDec) | is.na(LongMin))) %>%
  select(SampleEventID, LatitudeDec, LongitudeDec, LatDec, LatMin, LongDec, LongMin, FixedLon, FixedLat, Comments)

  # Out of range values - not needed for St Pete data currently since station locations are checked in MGID checks.
SampleEvent_range <- NULL
    # Flags SampleEvents that occur over 125 meters from the assigned FixedLocation 
#SampleEvent_range <- SampleEvent1 %>% rowwise() %>% mutate(DistFromFixed = distVincentySphere(c(LongitudeDec, LatitudeDec), c(FixedLon, FixedLat))) %>% filter(DistFromFixed > 125) %>% select(SampleEventID, LatitudeDec, LongitudeDec, FixedLat, FixedLon, DistFromFixed)
  
## Water Quality #
  # Unexpected Null values
null_WQs <- filter(SampleEventWQ1, is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(Depth) | is.na(SampleDepth) | is.na(PercentDissolvedOxygen)) %>% 
  filter(!grepl(paste(c("ame as", "ame WQ", "ame Water", "ame water"), collapse = '|'), Comments)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Temperature, Salinity, DissolvedOxygen, PercentDissolvedOxygen, pH, Comments)

  # Out of range values
Temp_range <- filter(SampleEventWQ1, Temperature < 10 | Temperature > 33) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Temperature, Comments)
Sal_range <- filter(SampleEventWQ1, Salinity < 0.5 | Salinity > 38) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Salinity, Comments)
DO_range <- SampleEventWQ1 %>% 
  mutate(DO.Sat = DO.saturation(DO.mgl = DissolvedOxygen, temp.C = Temperature, elevation.m = 0, salinity = Salinity)) %>%
  filter(DO.Sat < 0.50 | DO.Sat > 1.50) %>%
  mutate(DO.Sat = percent(DO.Sat, accuracy = 1)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, PercentDissolvedOxygen, DO.Sat, Comments)
DOPct_range <- SampleEventWQ1 %>% 
  filter(PercentDissolvedOxygen < 20 | PercentDissolvedOxygen > 150) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, PercentDissolvedOxygen, Comments)
pH_range <- filter(SampleEventWQ1, pH < 7.0 | pH > 8.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, pH, Comments)
Depth_range <- filter(SampleEventWQ1, Depth < 0 | Depth > 3.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
SampleDepth_range <- filter(SampleEventWQ1, SampleDepth < 0 | SampleDepth > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
Secchi_range <- filter(SampleEventWQ1, Secchi < 0 | Secchi > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Secchi, Comments)
TurbidityYSI_range <- filter(SampleEventWQ1, TurbidityYSI < -2 | TurbidityYSI > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityYSI, Comments)
TurbidityHach_range <- filter(SampleEventWQ1, TurbidityHach < -2 | TurbidityHach > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityHach, Comments)

## SurveyQuadrat #
  # Unexpected Null values

# We should change it in ODIN so that empty strings aren't sent. They should be null instead. Then the following line won't be needed
SurveyQuadrat1$Comments <- ifelse(nchar(SurveyQuadrat1$Comments) == 0, NA, SurveyQuadrat1$Comments) 

null_SurveyQuads <- if(EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW") {
  filter(SurveyQuadrat1, is.na(NumLive) | is.na(NumDead) & !is.na(Comments)) %>%
    select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, NumDrills, Comments)
  } else if(EstuaryCode == "CR") {
    filter(SurveyQuadrat1, (QuadratNumber < 11 & (is.na(NumLive) | is.na(NumDead)) & !is.na(Comments)) | (QuadratNumber > 10 & (is.na(NumLive) | is.na(NumDead) | is.na(TotalVolume) | is.na(TotalWeight)) & !is.na(Comments))) %>%
    select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, NumDrills, Comments)
  } else {
  filter(SurveyQuadrat1, is.na(NumLive) | is.na(NumDead) | is.na(TotalVolume) | is.na(TotalWeight) & !is.na(Comments)) %>%
  select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, NumDrills, Comments)
}

  # Out of range values
SurveyQuad_range <- if(EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW") {
  filter(SurveyQuadrat1, NumLive < 0 | NumLive > 900 | NumDead < 0 | NumDead > 500) %>%
    select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, Comments)
} else if (EstuaryCode == "CR"){
  filter(SurveyQuadrat1, (QuadratNumber < 11 & (NumLive < 0 | NumLive > 900 | NumDead < 0 | NumDead > 500)) |(QuadratNumber > 10 & (NumLive < 0 | NumLive > 900 | NumDead < 0 | NumDead > 500 | TotalVolume < 0.25 | 
           TotalVolume > 5.5 | TotalWeight < 0.1 | TotalWeight > 10.00))) %>%
    select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, Comments)
} else {
  filter(SurveyQuadrat1, NumLive < 0 | NumLive > 900 | NumDead < 0 | NumDead > 500 | TotalVolume < 0.25 | 
           TotalVolume > 5.5 | TotalWeight < 0.1 | TotalWeight > 10.00) %>%
    select(QuadratID, NumLive, NumDead, TotalVolume, TotalWeight, Comments)
}

## SurveySH #
  # Unexpected Null values

# We should change it in ODIN so that empty strings aren't sent. They should be null instead. Then the following line won't be needed
SurveySH1$Comments <- ifelse(nchar(SurveySH1$Comments) == 0, NA, SurveySH1$Comments) 

null_SurveySH <- left_join(SurveyQuadrat1, SurveySH1, by = c("QuadratID")) %>%
  rename("Comments" = "Comments.x") %>%
  select(ShellHeightID, ShellHeight, NumLive, Comments) %>%
  filter(is.na(ShellHeight) & NumLive != 0) 

  # Out of range values
SurveySH_range <- filter(SurveySH1, ShellHeight < 1 | ShellHeight > 150) %>%
  select(ShellHeightID, ShellHeight, Comments) 

  # Check for mismatch in number live and number measured. 
initialSHmeasurement <- filter(SurveySH1, substring(ShellHeightID, 29, 31) == "001") %>%
  rename("InitialSH" = "ShellHeight") # Pulls in the initial SH for each quadrat

SHmeasures <- as.data.frame(table(SurveySH1$QuadratID)) %>% # Counts up the number of SH measurements that were made
  rename("QuadratID" = "Var1",
         "NumMeasured" = "Freq") %>%
  left_join(SurveyQuadrat1, initialSHmeasurement, by = c("QuadratID")) %>%
  left_join(initialSHmeasurement, by = c("QuadratID")) %>%
  select(QuadratID, QuadratNumber, NumLive, NumMeasured, InitialSH, Comments.x) 

if(EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW"){
  Over10Measured <- SHmeasures %>% filter(NumMeasured > 10) %>% mutate(ErrorColumn = "Over 10 measured")
} else {
    Over50Measured <- SHmeasures %>% filter(NumMeasured > 50) %>% mutate(ErrorColumn = "Over 50 measured")
    }

if(EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW"){
  TooManyTooFew <- SHmeasures %>% filter(NumLive != NumMeasured) %>% 
    filter(!(NumLive > 10 & NumMeasured == 10)) %>% 
    filter(!(is.na(InitialSH) & NumLive == 0 & NumMeasured == 1)) %>%
    mutate(ErrorColumn = "Too many or too few measured")
} else {
    TooManyTooFew <- SHmeasures %>% filter(NumLive != NumMeasured) %>% 
    filter(!(NumLive > 50 & NumMeasured == 50)) %>% 
    filter(!(is.na(InitialSH) & NumLive == 0 & NumMeasured == 1)) %>%
    mutate(ErrorColumn = "Too many or too few measured")
}

if(EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW"){
  SHMismatch <- union(Over10Measured, TooManyTooFew) %>% arrange(QuadratID)
}else{
  SHMismatch <- union(Over50Measured, TooManyTooFew) %>% arrange(QuadratID)
  }

rm(initialSHmeasurement, SHmeasures, Over50Measured, TooManyTooFew) # deletes data frames no longer needed

## Set error messages #

if (nrow(null_SampleEvents) > 0) {
  Mess_null_SampleEvents = ""
} else {
  Mess_null_SampleEvents = "Congratulations! No unexpected null values detected."
}
  
if (nrow(null_WQs) > 0) {
  Mess_null_WQs = ""
} else {
  Mess_null_WQs = "Congratulations! No unexpected null values detected."
}

if (nrow(null_SurveyQuads) > 0) {
  Mess_null_SurveyQuads = ""
} else {
  Mess_null_SurveyQuads = "Congratulations! No unexpected null values detected."
}

if (nrow(null_SurveySH) > 0) {
  Mess_null_SurveySHs = ""
} else {
  Mess_null_SurveySHs = "Congratulations! No unexpected null values detected."
}

if (length(SampleEvent_range) == 0) {
  MessSampleEvent_ranges = "Congratulations! No out of range values detected."
} else {
  MessSampleEvent_ranges = ""
}

if (nrow(Temp_range) > 0 | nrow(Sal_range) > 0 | nrow(DO_range) > 0 | nrow(pH_range) > 0 | nrow(Depth_range) > 0 | nrow(SampleDepth_range) > 0 | nrow(Secchi_range) > 0 | nrow(TurbidityYSI_range) > 0 | nrow(TurbidityHach_range)) {
  MessWQ_ranges = ""
} else {
  MessWQ_ranges = "Congratulations! No out of range values detected."
}

if (nrow(SurveyQuad_range) > 0) {
  MessSurveyQuad_ranges = ""
} else {
  MessSurveyQuad_ranges = "Congratulations! No out of range values detected."
}

if (nrow(SurveySH_range) > 0 | nrow(SHMismatch) > 0) {
  MessSurveySH_ranges = ""
} else {
  MessSurveySH_ranges = "Congratulations! No out of range values detected."
}
```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d.%B.%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! SampleEvents must have 15 child records unless a valid comment is present.")}`

`r if (nrow(ERR_Table3a) > 0 & EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW") {kable(ERR_Table3a, caption = "Childless Primary Keys. SampleEvents must have 15 child records unless a valid comment is present.")}`
`r if (nrow(ERR_Table3a) > 0 & EstuaryCode == "TB") {kable(ERR_Table3a, caption = "Childless Primary Keys. SampleEvents must have 5 child records unless a valid comment is present.")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SurveyQuadrat_nulls) > 0) {kable(SurveyQuadrat_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SurveySH_nulls) > 0) {kable(SurveySH_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Sample Event ---</h4>

<p2>`r Mess_null_SampleEvents`</p2>

`r if (nrow(null_SampleEvents) > 0) {kable(null_SampleEvents, caption = "Null Sample Event Data. Comment Required for all Null values")}`

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment Required for all Null values")}`

<h4>--- Survey Quadrats ---</h4>

<p2>`r Mess_null_SurveyQuads`</p2>

`r if (nrow(null_SurveyQuads) > 0) {kable(null_SurveyQuads, caption = "Null Survey Quadrat Data. Comment Required for all Null values")}`

<h4>--- Survey Shell Heights ---</h4>

<p2>`r Mess_null_SurveySHs`</p2>

`r if (nrow(null_SurveySH) > 0) {kable(null_SurveySH, caption = "Null Survey Shell Height Data. Null values should only be recorded when no oysters were measured. ShellHeightID should end _001 and NumLive should be 0")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.

<h4>--- Sample Event ---</h4>

<p2>`r MessSampleEvent_ranges`</p2>

`r if (length(SampleEvent_range) == 0) {kable(SampleEvent_range, caption = "If distance from Fixed Location needs to be checked, update code for SampleEvent_range.")}`
`r if (length(SampleEvent_range) > 0) {kable(SampleEvent_range, caption = "Out of range distance from Fixed Location. Expected range is 125 meters. Comment required for out of range values.")}`

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 33.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 38.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range dissolved oxygen data. Expected calculated range is 50% to 120% saturation. Comment required for out of range values.")}`

`r if (nrow(DOPct_range) > 0) {kable(DOPct_range, caption = "Out of range percent dissolved oxygen data. Expected range is 20% to 150% saturation. Comment required for out of range values.")}`

`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Survey Quadrat ---</h4>

<p2>`r MessSurveyQuad_ranges`</p2>

`r if (nrow(SurveyQuad_range) > 0 & EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW") {kable(SurveyQuad_range, caption = "Out of range Quadrat data. Expected range for NumLive is 0 to 900. Expected range for NumDead is 0 to 500. Comment required for out of range values.")} else {kable(SurveyQuad_range, caption = "Out of range Quadrat data. Expected range for NumLive is 0 to 900. Expected range for NumDead is 0 to 500. Expected range for TotalVolume is 0.05 to 5.5 L. Expected range for TotalWeight is 0.10 to 10.00 kg. Comment required for out of range values.")}`

<h4>--- Survey Shell Heights ---</h4>

<p2>`r MessSurveySH_ranges`</p2>

`r if (nrow(SurveySH_range) > 0) {kable(SurveySH_range, caption = "Out of range Shell Height data. Expected range for ShellHeight is 1 to 150 mm. Cannot be 0. Comment required for out of range values.")}`

`r if (nrow(SHMismatch) > 0 & EstuaryCode == "SL" | EstuaryCode == "LX" | EstuaryCode == "LW") {kable(SHMismatch, caption = "Mismatched Shell Height and Quadrat data. NumLive must equal NumMeasured, unless: NumLive = 0 & NumMeasured = 1 & InitialSH is NULL -OR- NumLive is greater than 10 and NumMeasured = 10. Comment required for mismatched values.")} else {kable(SHMismatch, caption = "Mismatched Shell Height and Quadrat data. NumLive must equal NumMeasured, unless: NumLive = 0 & NumMeasured = 1 & InitialSH is NULL -OR- NumLive is greater than 50 and NumMeasured = 50. Comment required for mismatched values.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

EXECUTE [dbo].[spChecksSurvey]
	@CheckStart = \'`r CheckStart`\',
	@CheckEnd = \'`r CheckEnd`\',
	@EstuaryCode = \'`r EstuaryCode`\',
	@DataManager = \'`r DataManager`\';
	
`r knit_exit()`

```{sql SQL code, eval=FALSE, include=FALSE}
--- This code creates a stored procedure in the database. 
-- To do so, copy and paste this code VERBATIM into SSMS
-- DO NOT RUN THIS CODE WITH R --

CREATE PROCEDURE [dbo].[spChecksSurvey](
	@CheckStart AS DATE,
	@CheckEnd AS DATE,
	@EstuaryCode AS VARCHAR(2),
	@DataManager AS VARCHAR(max)
	)
AS
BEGIN
	DECLARE @CompletedDate DATE;
	SET @CompletedDate = cast(getDate() as date);

	IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
	BEGIN
    DROP TABLE #ValidTrips;
  END

	CREATE TABLE #ValidTrips (
		TripID VARCHAR(50)
	);

	INSERT INTO #ValidTrips (TripID)
	SELECT TripID
	FROM dbo.TripInfo
	WHERE TripDate >= @CheckStart AND TripDate <= @CheckEnd
	AND DataStatus = 'Proofed' AND TripID like CONCAT(@EstuaryCode, 'SRVY%');

	-- Query the TripInfo table using the temporary table
	UPDATE dbo.TripInfo 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEvent table using the temporary table
	UPDATE dbo.SampleEvent 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEventWQ table using the temporary table
	UPDATE dbo.SampleEventWQ 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

  -- Query the SurveyQuadrat table using the temporary table
  UPDATE dbo.SurveyQuadrat 
  SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
  WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));
  
  -- Query the SurveySH table using the temporary table
  UPDATE dbo.SurveySH 
  SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
  WHERE QuadratID IN (SELECT QuadratID FROM SurveyQuadrat WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips)));

  -- Insert the Completed data into hsdb, and DELETE FROM dbo
  INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SurveyQuadrat SELECT * FROM SurveyQuadrat WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SurveyQuadrat WHERE DataStatus = 'Completed';
  
  INSERT INTO hsdb.SurveySH SELECT * FROM SurveySH WHERE DataStatus = 'Completed';
  
  DELETE FROM dbo.SurveySH WHERE DataStatus = 'Completed';

END

```