---
title: "Wave Motion Data Checks"
output:
  html_document:
knit: (function(inputFile, encoding) {rmarkdown::render(input = inputFile, encoding = encoding, output_file = paste0(substr(inputFile, 1, nchar(inputFile)-4), "_", Sys.Date(), '.html')) })
---

```{r VariableSet, echo = FALSE, warning = FALSE, message = FALSE}
# Set your variables
CheckStart <- as.Date("2023-01-01")  # Start Date for Checks
CheckEnd <- as.Date("2023-12-31")  # End Date for Checks
EstuaryCode = "TB"  # Estuary Code. Use 2-letter code in Primary Keys
DataManager = "Erica Levine"
Database = "OystersEL_240119"
```

```{r PackageLoad, echo = FALSE, warning = FALSE, message = FALSE}
# Load necessary R packages and configure chunks
library(tidyverse)
library(odbc)
library(DBI)
library(dbplyr)
library(lubridate)
library(rMR)
library(scales)
library(knitr)

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

```

```{css}
/* Sets the fonts for the RMarkdown output */
p {
font-size: 8pt;
}

p2 {
font-weight: bold;
}

h1 {
font-size: 18pt;
font-weight: bold;
}

h2 {
font-size: 14pt;
font-weight: bold;
}

h3 {
font-size: 12pt;
font-style: italic;
}

h4 {
font-size: 10pt;
text-indent: 5%;
font-weight: bold;
}
```

```{r DatabaseDownload}
# Connect to Local database server and pull all necessary data, then close connection 
con <- dbConnect(odbc(),
                    Driver = "SQL Server", 
                    Server = "localhost\\ERICALOCALSQL",
                    Database = Database,
                    Authentication = "ActiveDirectoryIntegrated")

dboFixedLocations <- tbl(con,in_schema("dbo", "FixedLocations")) %>%
  collect() %>% 
  filter(Estuary == EstuaryCode)

hsdbTripInfo <- tbl(con,in_schema("hsdb", "TripInfo")) %>%
  collect() 

dboTripInfo <- tbl(con,in_schema("dbo", "TripInfo")) %>%
  collect() 
  
hsdbSampleEvent <- tbl(con,in_schema("hsdb", "SampleEvent")) %>%
  collect() 
  
dboSampleEvent <- tbl(con,in_schema("dbo", "SampleEvent")) %>%
  collect() 

hsdbSampleEventWQ <- tbl(con,in_schema("hsdb", "SampleEventWQ")) %>%
  collect() 

dboSampleEventWQ <- tbl(con,in_schema("dbo", "SampleEventWQ")) %>%
  collect() 

hsdbWave <- tbl(con,in_schema("hsdb", "Wave")) %>%
  collect() 

dboWave <- tbl(con,in_schema("dbo", "Wave")) %>%
  collect()

DBI::dbDisconnect(con)

```

```{r DataFilters}
# Filter data frames so that only data collected from Wave motion trips in the specified Estuary, in the correct date range, which have been Proofed, are present.
FixedLocations1 <- dboFixedLocations %>% 
  mutate(StationNumber = as.numeric(StationNumber)) %>% 
  select(FixedLocationID,
         Estuary,
         SectionName, 
         StationNumber) %>% 
  distinct()
          
TripInfo1 <- dboTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & TripType == "Wave Motion" & DataStatus == "Proofed") %>%
  arrange(TripID)

TripInfo2 <- TripInfo1 %>%
  select(TripID, TripDate, Comments) %>%
  arrange(TripID)

SampleEvent1 <- dboSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventID, 19, 22)) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "WAVE" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEvent1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber)

SampleEventWQ1 <- dboSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(SampleEventWQID, 19, 22)) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventWQID,3,6) == "WAVE" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, SampleEventWQ1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, SampleEventWQID)

Wave1 <- dboWave %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d"),
         FixedLocationID = substring(WaveID, 19, 22)) %>%
         #NumDays = as.numeric(interval(DeployedDate, TripDate), "days")) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "WAVE" & DataStatus == "Proofed") %>%
  left_join(FixedLocations1, Wave1, by = c("FixedLocationID")) %>%
  arrange(TripDate, StationNumber, WaveID) 

hsdbTripInfo <- hsdbTripInfo %>% 
  filter(substring(TripID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & TripType == "Wave Motion")  %>%
  arrange(TripID)

hsdbSampleEvent <- hsdbSampleEvent %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "WAVE") %>%
  arrange(TripDate)

hsdbSampleEventWQ <- hsdbSampleEventWQ %>% 
  mutate(TripDate = as.Date(substring(SampleEventWQID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventWQID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventWQID,3,6) == "WAVE") %>%
  arrange(TripDate)

hsdbWave <- hsdbWave %>% 
  mutate(TripDate = as.Date(substring(SampleEventID, 8, 15), format = "%Y%m%d")) %>%
  filter(substring(SampleEventID,1,2) == EstuaryCode & TripDate >= CheckStart & TripDate < CheckEnd & substring(SampleEventID,3,6) == "WAVE") %>%
  arrange(TripDate)

```

```{r DatabaseErrors}
### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the dbo schema
ERR_Table1 <- data.frame()
ERR_Table1a <- data.frame()
ERR_Table1b <- data.frame()
ERR_Table1c <- data.frame()
ERR_Table1d <- data.frame()

if (nrow(TripInfo1[duplicated(TripInfo1$TripID), ]) > 0) {
  ERR_Table1a <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "TripInfo", TripInfo1[duplicated(TripInfo1$TripID), ])) %>% 
    mutate(PrimaryKey = TripID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEvent1[duplicated(SampleEvent1$SampleEventID), ]) > 0) {
  ERR_Table1b <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEvent", SampleEvent1[duplicated(SampleEvent1$SampleEventID), ])) %>% 
    mutate(PrimaryKey = SampleEventID) %>%
    select(schema, Table, PrimaryKey)
}

if (nrow(SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ]) > 0) {
  ERR_Table1c <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "SampleEventWQ", SampleEventWQ1[duplicated(SampleEventWQ1$SampleEventWQID), ])) %>% 
    mutate(PrimaryKey = SampleEventWQID) %>% 
    select(schema, Table, PrimaryKey)
}

if (nrow(Wave1[duplicated(Wave1$WaveID), ]) > 0) {
  ERR_Table1d <- bind_rows(ERR_Table1, data.frame(schema = "dbo", Table = "Wave", Wave1[duplicated(Wave1$WaveID), ])) %>% 
    mutate(PrimaryKey = WaveID) %>%
    select(schema, Table, PrimaryKey)
}

### DATABASE ERRORS ###
# Ensure the Primary Keys are unique in the hsdb schema
ERR_Tablex <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, Wave1$WaveID)
dest <- list(hsdbTripInfo$TripID, hsdbSampleEvent$SampleEventID, hsdbSampleEventWQ$SampleEventWQID, hsdbWave$WaveID)
tabl <- list("TripInfo", "SampleEvent", "SampleEventWQ", "Wave Motion")

# Loop through values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if ((check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Tablex <- rbind(ERR_Tablex, data.frame(schema = "hsdb", Table = tabl[[i]], PrimaryKey = check_id))
    }
  }
}

ERR_Table1 <- rbind(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Tablex)
rm(ERR_Table1a, ERR_Table1b, ERR_Table1c, ERR_Table1d, ERR_Tablex)


### DATABASE ERRORS ###
# Ensure the Foreign Keys are not orphans
# Create an empty data frame ERR_Table
ERR_Table2 <- data.frame()
sorc <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Wave1$SampleEventID)
dest <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ", "Wave")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
  # Check if the trip_id exists in TripInfo$TripID
    if (!(check_id %in% dest[[i]])) {
    # Add trip_id to ERR_Table
      ERR_Table2 <- rbind(ERR_Table2, data.frame(Table = tabl[[i]], OrphanForeignKey = check_id))
    }
  }
}
ERR_Table2 <- distinct(ERR_Table2) 

### DATABASE ERRORS ###
# Ensure the Primary Keys are not childless
ERR_Table3 <- data.frame()
sorc <- list(TripInfo1$TripID, SampleEvent1$SampleEventID, SampleEvent1$SampleEventID)
dest <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Wave1$SampleEventID)
tabl <- list("TripInfo", "SampleEvent", "SampleEvent")

# Loop through SampleEvent$TripID values
for (i in seq_along(sorc)) {
  for (j in seq_along(sorc[[i]])) {
    check_id <- sorc[[i]][j]
    if (!(check_id %in% dest[[i]])) {
      ERR_Table3 <- rbind(ERR_Table3, data.frame(Table = tabl[[i]], ChildlessPrimaryKey = check_id))
    }
  }
}
ERR_Table3 <- distinct(ERR_Table3) 

### DATABASE ERRORS ###
# Ensure that Primary Keys and Foreign Keys have been formed correctly
ERR_Table4 <- data.frame()
pkid <- list(SampleEvent1$SampleEventID, SampleEventWQ1$SampleEventWQID, Wave1$WaveID)
fkid <- list(SampleEvent1$TripID, SampleEventWQ1$SampleEventID, Wave1$SampleEventID)
tabl <- list("SampleEvent", "SampleEventWQ", "Wave")
numb <- list(17, 24, 24)

for (i in seq_along(pkid)) {
  for (j in seq_along(fkid[[i]])) {
    check_fkid <- fkid[[i]][j]
    check_pkid <- substring(pkid[[i]][j],1,numb[[i]])
    if (check_fkid != check_pkid) {
      ERR_Table4 <- rbind(ERR_Table4, data.frame(Table = tabl[[i]], PrimaryKey = pkid[[i]][j], ForeignKey = check_fkid))
    }
  }
}

### DATABASE ERRORS ###
# Ensure that any field that MUST have a value is not null
TripInfo_nulls <- filter(TripInfo1, is.na(TripID) | is.na(TripType) | is.na(TripDate) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(TripID, TripDate, TripType, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEvent_nulls <- filter(SampleEvent1, is.na(SampleEventID) | is.na(TripID) | is.na(FixedLocationID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventID, TripID, FixedLocationID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

SampleEventWQ_nulls <- filter(SampleEventWQ1, is.na(SampleEventWQID) | is.na(SampleEventID) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(SampleEventWQID, SampleEventID, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

Wave_nulls <- filter(Wave1, is.na(WaveID) | is.na(SampleEventID) | is.na(InitialWeight) | is.na(WetWeight) | is.na(DryWeight) | is.na(EnteredBy) | is.na(DateEntered) | is.na(ProofedBy) | is.na(DateProofed) ) %>%
  select(WaveID, SampleEventID, InitialWeight, WetWeight, DryWeight, EnteredBy, DateEntered, ProofedBy, DateProofed, Comments)

# Remove unneeded data frames and values

rm(dboFixedLocations, dboWave, dboSampleEvent, dboSampleEventWQ, dboTripInfo, dest, FixedLocations1, hsdbWave, hsdbSampleEvent, hsdbSampleEventWQ, hsdbTripInfo, fkid, pkid, numb, sorc, tabl, check_id, i, j)

# Set Error Messages for Database Errors

if (nrow(ERR_Table1) > 0 | nrow(ERR_Table2) > 0 | nrow(ERR_Table3) > 0 | nrow(ERR_Table4) > 0 | nrow(TripInfo_nulls) > 0 | nrow(SampleEvent_nulls) > 0 | nrow(SampleEventWQ_nulls) > 0 | nrow(Wave_nulls) > 0) {
  MessERR_Tables1 = "STOP! These are critical errors that must be fixed before proceeding!"
  MessERR_Tables2 = ""
} else {
  MessERR_Tables1 = ""
  MessERR_Tables2 = "Congratulations! No Database errors found. Primary Keys are unique and not childless. Foreign Keys are not orphans and are properly formed. All critical fields contain data. You may proceed."
}
```

```{r Data Errors}
### DATA ERRORS ###
#Value ranges below represent historically high or low values. Actual values can be outside that range and may or may not require a Comment, unless noted otherwise. 

## TripInfo #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## SampleEvent #
  # There are no fields that require a Comment if they are NULL.
  # There are no out of range values for this table

## Water Quality #
  # Unexpected Null values
null_WQs <- filter(SampleEventWQ1, is.na(Temperature) | is.na(Salinity) | is.na(DissolvedOxygen) | is.na(pH) | is.na(Depth) | is.na(SampleDepth)) %>% filter(!grepl(paste(c("ame as", "ame WQ", "ame Water", "ame water"), collapse = '|'), SampleEventWQ1$Comments)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Temperature, Salinity, DissolvedOxygen, pH, Comments)

  # Out of range values
Temp_range <- filter(SampleEventWQ1, Temperature < 10 | Temperature > 33) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Temperature, Comments)
Sal_range <- filter(SampleEventWQ1, Salinity < 0.5 | Salinity > 38) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Salinity, Comments)
DO_range <- SampleEventWQ1 %>% 
  mutate(DO.Sat = DO.saturation(DO.mgl = DissolvedOxygen, temp.C = Temperature, elevation.m = 0, salinity = Salinity)) %>%
  filter(DO.Sat < 0.50 | DO.Sat > 1.20) %>%
  mutate(DO.Sat = percent(DO.Sat, accuracy = 1)) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, DissolvedOxygen, DO.Sat, Comments)
pH_range <- filter(SampleEventWQ1, pH < 7.0 | pH > 8.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, pH, Comments)
Depth_range <- filter(SampleEventWQ1, Depth < 0 | Depth > 3.5) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
SampleDepth_range <- filter(SampleEventWQ1, SampleDepth < 0 | SampleDepth > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Comments)
Secchi_range <- filter(SampleEventWQ1, Secchi < 0 | Secchi > Depth) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, Depth, Secchi, Comments)
TurbidityYSI_range <- filter(SampleEventWQ1, TurbidityYSI < -2 | TurbidityYSI > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityYSI, Comments)
TurbidityHach_range <- filter(SampleEventWQ1, TurbidityHach < -2 | TurbidityHach > 30) %>%
  select(SampleEventWQID, StationNumber, SampleDepth, TurbidityHach, Comments)

## Wave #
  # Unexpected Null values

# We should change it in ODIN so that empty strings aren't sent. They should be null instead. Then the following line won't be needed
Wave1$Comments <- ifelse(nchar(Wave1$Comments) == 0, NA, Wave1$Comments) 
null_Recs <- filter(Wave1, (is.na(WetWeight) | is.na(DryWeight)) & !is.na(Comments)) %>%
  select(TripDate, StationNumber, WaveID, InitialWeight, WetWeight, DryWeight, Comments)

  # Out of range values
Initial_range <- filter(Wave1, InitialWeight < 50 | InitialWeight > 230) %>%
  select(TripDate, StationNumber,  WaveID, InitialWeight, WetWeight, DryWeight, Comments)
Wet_range <- filter(Wave1, WetWeight <= 0 & WetWeight > InitialWeight) %>%
  select(TripDate, StationNumber,  WaveID, InitialWeight, WetWeight, DryWeight, Comments)
Dry_range <- filter(Wave1, DryWeight > WetWeight) %>%
  select(TripDate, StationNumber,  WaveID, InitialWeight, WetWeight, DryWeight, Comments)
  
if (nrow(null_WQs) > 0) {
  Mess_null_WQs = ""
} else {
  Mess_null_WQs = "Congratulations! No unexpected null values detected."
}

if (nrow(null_Recs) > 0) {
  Mess_null_Recs = ""
} else {
  Mess_null_Recs = "Congratulations! No unexpected null values detected."
}

if (nrow(Temp_range) > 0 | nrow(Sal_range) > 0 | nrow(DO_range) > 0 | nrow(pH_range) > 0 | nrow(Depth_range) > 0 | nrow(SampleDepth_range) > 0 | nrow(Secchi_range) > 0 | nrow(TurbidityYSI_range) > 0 | nrow(TurbidityHach_range)) {
  MessWQ_ranges = ""
} else {
  MessWQ_ranges = "Congratulations! No out of range values detected."
}

if (nrow(Initial_range) > 0 | nrow(Wet_range) > 0  | nrow(Dry_range) > 0) {
  MessRec_ranges = ""
} else {
  MessRec_ranges = "Congratulations! No out of range values detected."
}
```

These data checks were run on trips occurring between
<p2>`r CheckStart`</p2> and <p2>`r CheckEnd`</p2>\
by <p2>`r DataManager`</p2> on
<p2>`r format(Sys.Date(), "%d.%B.%Y")`</p2> using database <p2> `r Database`</p2>.

`r kable(TripInfo2, caption = "Data from these trips is included in these checks")`

<h2>Database Errors:</h2>

<h1>`r MessERR_Tables1`</h1> <p2>`r MessERR_Tables2`</p2>

`r if (nrow(ERR_Table1) > 0) {kable(ERR_Table1, caption = "Duplicate Primary Keys. Primary Keys MUST be unique!")}`

`r if (nrow(ERR_Table2) > 0) {kable(ERR_Table2, caption = "Orphan Foreign Keys. Foreign Keys MUST have a parent!")}`

`r if (nrow(ERR_Table3) > 0) {kable(ERR_Table3, caption = "Childless Primary Keys. Primary Keys MUST have at least one child record! Only exception is on DEPLOY ONLY events.")}`

`r if (nrow(ERR_Table4) > 0) {kable(ERR_Table4, caption = "Malformed Keys. Primary Keys MUST contain its Foreign Key!")}`

`r if (nrow(TripInfo_nulls) > 0) {kable(TripInfo_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEvent_nulls) > 0) {kable(SampleEvent_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(SampleEventWQ_nulls) > 0) {kable(SampleEventWQ_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

`r if (nrow(Wave_nulls) > 0) {kable(Wave_nulls, caption = "Critical Nulls. These fields MUST contain data!")}`

<h2>Data Errors:</h2>

<h3>~ ~ ~ ~ ~ ~ ~ Unexpected null values ~ ~ ~ ~ ~ ~ ~</h3>

The following fields are expected to either contain data or have a
comment explaining why the data is missing.

<h4>--- Water Quality ---</h4>

<p2>`r Mess_null_WQs`</p2>

`r if (nrow(null_WQs) > 0) {kable(null_WQs, caption = "Null Water Quality Data. Comment Required for all Null values")}`

<h4>--- Wave Motion ---</h4>

<p2>`r Mess_null_Recs`</p2>

`r if (nrow(null_Recs) > 0) {kable(null_Recs, caption = "Null Wave Motion Data. Comment Required for all Null values")}`

<h3>~ ~ ~ ~ ~ ~ ~ Out of range values ~ ~ ~ ~ ~ ~ ~ </h3>

Value ranges below represent historically high or low values. Actual
values can be outside that range and may or may not require a Comment.
Weights ranges are based on logical dissolution expectations and values outside of the range require a Comment.

<h4>--- Water Quality ---</h4>

<p2>`r MessWQ_ranges`</p2>

`r if (nrow(Temp_range) > 0) {kable(Temp_range, caption = "Out of range temperature data. Expected range is 10.0°C to 33.0°C. Comment required for out of range values.")}`

`r if (nrow(Sal_range) > 0) {kable(Sal_range, caption = "Out of range Salinity data. Expected range is 0.5 to 35.0 ppt. Comment required for out of range values.")}`

`r if (nrow(DO_range) > 0) {kable(DO_range, caption = "Out of range dissolved oxygen data. Expected range is 50% to 120% saturation. . Comment required for out of range values.")}`

`r if (nrow(pH_range) > 0) {kable(pH_range, caption = "Out of range pH data. Expected range is 7.0 to 8.5. Comment required for out of range values.")}`

`r if (nrow(Depth_range) > 0) {kable(Depth_range, caption = "Out of range depth data. Expected range is 0.0 to 3.5 m. Cannot be less than 0. Comment required for out of range values.")}`

`r if (nrow(SampleDepth_range) > 0) {kable(SampleDepth_range, caption = "Out of range Sample depth data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(Secchi_range) > 0) {kable(Secchi_range, caption = "Out of range Secchi data. Expected range is 0.0 m to 'Depth'. Cannot be less than 0 or exceed 'Depth'")}`

`r if (nrow(TurbidityYSI_range) > 0) {kable(TurbidityYSI_range, caption = "Out of range Turbidity data. Expected range is -2.0 to 30 NTU. Comment required for out of range values.")}`

<h4>--- Wave Motion ---</h4>

<p2>`r MessRec_ranges`</p2>

`r if (nrow(Initial_range) > 0) {kable(Initial_range, caption = "Out of range initial weight. Expected range is 50g to 230g. Comment required for out of range values.")}`

`r if (nrow(Wet_range) > 0) {kable(Wet_range, caption = "Out of range wet weight. Expected range is 0 to Initial weight. Comment required for out of range values.")}`

`r if (nrow(Dry_range) > 0) {kable(Dry_range, caption = "Out of range dry weight. Expected range is less than the Wet weight. Comment required for out of range values.")}`

<h2>SQL Code:</h2>

If there are no Database Errors detected and all Data Errors have been
addressed, you may use the following SQL code to Complete these data.
This code will update the DataStatus, CompletedBy, and DateCompleted
fields; it will copy the data to the hsdb schema; and it will remove the
data from the dbo schema.

<p2>It is recommended that you test this query in your local instance
BEFORE executing it on fwcsqlint.</p2>

EXECUTE [dbo].[spChecksWave]
	@CheckStart = \'`r CheckStart`\',
	@CheckEnd = \'`r CheckEnd`\',
	@EstuaryCode = \'`r EstuaryCode`\',
	@DataManager = \'`r DataManager`\';

`r knit_exit()`

```{sql SQL code, eval=FALSE, include=FALSE}
--- This code creates a stored procedure in the database. 
-- To do so, copy and paste this code VERBATIM into SSMS
-- DO NOT RUN THIS CODE WITH R --

CREATE PROCEDURE [dbo].[spChecksWave](
	@CheckStart AS DATE,
	@CheckEnd AS DATE,
	@EstuaryCode AS VARCHAR(2),
	@DataManager AS VARCHAR(max)
	)
AS
BEGIN
	DECLARE @CompletedDate DATE;
	SET @CompletedDate = cast(getDate() as date);

	IF OBJECT_ID('tempdb..#ValidTrips') IS NOT NULL
	BEGIN
		DROP TABLE #ValidTrips;
	END

	CREATE TABLE #ValidTrips (
		TripID VARCHAR(50)
	);

	INSERT INTO #ValidTrips (TripID)
	SELECT TripID
	FROM TripInfo
	WHERE TripDate > @CheckStart AND TripDate < @CheckEnd
	AND DataStatus = 'Proofed' AND TripID like CONCAT(@EstuaryCode, 'WAVE%');

	-- Query the TripInfo table using the temporary table
	UPDATE TripInfo 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEvent table using the temporary table
	UPDATE SampleEvent 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE TripID IN (SELECT TripID FROM #ValidTrips);

	-- Query the SampleEventWQ table using the temporary table
	UPDATE SampleEventWQ 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

	-- Query the Wave table using the temporary table
	UPDATE Wave 
	SET DataStatus = 'Completed', CompletedBy = @DataManager, DateCompleted = @CompletedDate
	WHERE SampleEventID IN (SELECT SampleEventID FROM SampleEvent WHERE TripID IN (SELECT TripID FROM #ValidTrips));

	-- Insert the Completed data into hsdb, and DELETE FROM dbo
	INSERT INTO hsdb.TripInfo SELECT * FROM TripInfo WHERE DataStatus = 'Completed';

	DELETE FROM dbo.TripInfo WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.SampleEvent SELECT * FROM SampleEvent WHERE DataStatus = 'Completed';

	DELETE FROM dbo.SampleEvent WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.SampleEventWQ SELECT * FROM SampleEventWQ WHERE DataStatus = 'Completed';

	DELETE FROM dbo.SampleEventWQ WHERE DataStatus = 'Completed';

	INSERT INTO hsdb.Wave SELECT * FROM Wave WHERE DataStatus = 'Completed';

	DELETE FROM dbo.Wave WHERE DataStatus = 'Completed';

END

```
